---
title: "Compare Togo Data"
author: "Aditya Ramani"
date: "2023-08-02"
output: html_document
---

# Initial Setup
This chunk initializes the libraries and variables needed for the analysis code below. `data_folder` should be the path to the post-processed output of running `all_funcs_combined_togo.R` with 9000 iterations. You can post-process the data using code from `processRCSFilesTogo.R`. The relative path to the post-processed data (from the working directory) is expected to be `data/{prefecture}{folder variable}/`.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
set.seed(7281998)
library(dplyr)
library(ggplot2)
library(tidyr)
library(fastR2)
library(stringr)
library(gtable)
library(knitr)
library(kableExtra)
library(doParallel)
library(foreach)
library(data.table)
library(webshot)
library(gridExtra)
library(patchwork)
library(ggpattern)
knitr::knit_hooks$set(timeit = local({
  now = NULL
  function(before, options) {
    if (before) {
      now <<- Sys.time()
    } else {
      res = difftime(Sys.time(), now)
      now <<- NULL
      # use options$label if you want the chunk label as well
      paste('Time for this code chunk:', as.character(res))
    }
  }})
)
folder = "_agg_data_final_worm_revert/"
oti_folder_100 = "_agg_data_final_worm_revert_vary_abr_vc_100/"

run_version = "v9"
use_oti_100 <- FALSE
if (use_oti_100) {
  run_version = paste0(run_version, "_oti_100")
}
use_k4 <- FALSE
knitr::opts_knit$set(root.dir = dirname(getwd()))
```

## Actual Data
This code chunk sets up the read and processing files for the observed data.

The Togo data has been extracted from the following paper: Komlan K, Vossberg PS, Gantin RG, Solim T, Korbmacher F, Banla M, Padjoudoum K, Karabou P, Köhler C, Soboslay PT. Onchocerca volvulus infection and serological prevalence, ocular onchocerciasis and parasite transmission in northern and central Togo after decades of Simulium damnosum s.l. vector control and mass drug administration of ivermectin. PLoS Negl Trop Dis. 2018 Mar 1;12(3):e0006312. doi: 10.1371/journal.pntd.0006312. PMID: 29494606; PMCID: PMC5849363.
```{r basic_read_functions, timeit=TRUE}
# all data from tables in https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5849363/
togoMF <- function(combined_pop=TRUE) {
  # 2 years each side except for 7.5 (2.5y gap) and 70.5 (9.5y gap)
  ageGroups <- c(7.5, 13, 18, 23, 28, 33, 38, 43, 48, 53, 58, 70.5)
  male_pop <- c(96, 106, 31, 32, 58, 45, 42, 45, 37, 32, 29, 42)
  female_pop <- c(76, 106, 64, 86, 137, 90, 63, 44, 53, 30, 32, 38)
  mf_pos_male <- c(1, 1, 0, 2, 9, 6, 6, 4, 3, 2, 1, 1)
  mf_pos_female <- c(3, 3, 1, 4, 7, 7, 8, 3, 3, 0, 3, 4)
  wilson_lb_m <- c()
  wilson_ub_m <- c()
  wilson_lb_f <- c()
  wilson_ub_f <- c()
  for(i in 1:length(ageGroups)) {
    wilson_ci_m <- wilson.ci(mf_pos_male[i], male_pop[i])
    wilson_ci_f <- wilson.ci(mf_pos_female[i], female_pop[i])

    wilson_lb_m <- c(wilson_lb_m, wilson_ci_m[1])
    wilson_ub_m <- c(wilson_ub_m, wilson_ci_m[2])
    wilson_lb_f <- c(wilson_lb_f, wilson_ci_f[1])
    wilson_ub_f <- c(wilson_ub_f, wilson_ci_f[2])
  }
  
  data <- data.frame(age_groups=ageGroups, male_pop=male_pop, female_pop=female_pop, mf_pos_male=mf_pos_male, mf_pos_female=mf_pos_female,
                     mf_wilson_lb_m=wilson_lb_m, mf_wilson_ub_m=wilson_ub_m,
                     mf_wilson_lb_f=wilson_lb_f, mf_wilson_ub_f=wilson_ub_f) %>%
    mutate(mf_prev_male = mf_pos_male/male_pop,
           mf_prev_female=mf_pos_female/female_pop,
           mf_wilson_lb_m=ifelse(mf_wilson_lb_m < 0, 0, mf_wilson_lb_m),
           mf_wilson_lb_f=ifelse(mf_wilson_lb_f < 0, 0, mf_wilson_lb_f))
  
  if(combined_pop) {
    total_pop <- male_pop + female_pop
    total_mf_pos <- mf_pos_male + mf_pos_female
    wilson_lb <- c()
    wilson_ub <- c()
    for(i in 1:length(ageGroups)) {
      wilson_ci <- wilson.ci(total_mf_pos[i], total_pop[i])

      wilson_lb <- c(wilson_lb, wilson_ci[1])
      wilson_ub <- c(wilson_ub, wilson_ci[2])
    }
    data <- data %>% mutate(total_pop=total_pop, mf_pos_total=total_mf_pos, mf_wilson_lb=wilson_lb, mf_wilson_ub=wilson_ub) %>% 
      mutate(
        mf_prev = mf_pos_total/total_pop
      )
  }
  return(data)
}

togoOv16 <- function() {
  # 2 years each side except for 7.5 (2.5y gap) and 75.5 (4.5y gap)
  ageGroups <- c(7.5, 13, 18, 23, 28, 33, 38, 43, 48, 53, 58, 63, 68, 75.5)
  participants <- c(87, 76, 41, 44, 75, 58, 40, 27, 43, 24, 30, 13, 16, 2)
  ov16_pos <- c(13, 12, 7, 18, 31, 22, 20, 11, 15, 15, 17, 6, 9, 2)

  ageGroups <- c(0, 7.5, 13, 18, 23, 28, 33, 38, 43, 48, 53, 58, 63, 73)
  participants <- c(1, 87, 76, 41, 44, 75, 58, 40, 27, 43, 24, 30, 13, 18)
  ov16_pos <- c(0, 13, 12, 7, 18, 31, 22, 20, 11, 15, 15, 17, 6, 11)
  wilson_lb <- c()
  wilson_ub <- c()
  for(i in 1:length(ov16_pos)) {
    if(i==1) {
      wilson_lb <- c(wilson_lb, 0)
      wilson_ub <- c(wilson_ub, 0)
      next
    }
    wilson_ci <- wilson.ci(ov16_pos[i], participants[i])

    wilson_lb <- c(wilson_lb, wilson_ci[1])
    wilson_ub <- c(wilson_ub, wilson_ci[2])
  }
  data <- data.frame(age_groups=ageGroups, participants=participants, ov16_seropos=ov16_pos,
                     ov16_wilson_lb=wilson_lb, ov16_wilson_ub=wilson_ub) %>%
    mutate(ov16_seroprev = ov16_pos/participants, pct_pop=ifelse(age_groups==0, 0, participants/(sum(participants)-1)))
  return(data)
}

togoVillage <- function() {
  riverBasin <- c(rep('Oti', 3), rep('Keran', 4), rep('Mo', 4))
  # https://journals.plos.org/plosntds/article/figure?id=10.1371/journal.pntd.0006312.g002
  # https://www.citypopulation.de/en/togo/admin/
  prefecture <- c('OTI/KPENDJAL', 'OTI/KPENDJAL', 'OTI/KPENDJAL', #c('KPENDJAL', 'KPENDJAL', 'OTI',#
                  'Keran', 'Keran', 'Keran', 'Keran',
                  'Bassar', 'Bassar', 'Bassar', 'Bassar')
  village <- c('Pancerys', 'Boutchakou', 'Koukoumbou',
               'Goulbi', 'Tchitchira', 'Koutougou Solla', 'Kpantiiyagou',
               'Bawlensi', 'Mo-Village', 'Katcha-Konkomba', 'Saboundi')
  mfExamined <- c(140, 127, 57,
                  131, 146, 81, 181,
                  148, 151, 188, 105)
  mfPositive <- c(4, 1, 3,
                  15, 15, 11, 14,
                  0, 13, 5, 2)
  mfLB <- c(0, 0, 0, 
            7.5, 6.6, 8.6, 4.4,
            0, 4.9, 0, 0)
  mfUB <- c(6.6, 4.8, 11.2,
            15.4, 14.0, 18.5, 11.11,
            3.7, 12.2, 5.9, 6.3)
  ov16ElisaExaminedAllAges <- c(92, 92, 70,
                         92, 92, 79, 92,
                         NA, 22, NA, 13)
  ov16ElisaPositive <- c(10, 15, 9,
                         42, 42, 45, 46,
                         NA, 9, NA, 1)
  ov16ElisaLB <- c(4.4, 8.6, 4.8, 
                   35.5, 35.3, 45.8, 39.6,
                   NA, 18.6, NA, 0)
  ov16ElisaUB <- c(17.4, 24, 20.9,
                   56, 56, 68.1, 60.4,
                   NA, 63.2, NA, 24.4)
  # Age 5-10
  ov16ElisaChildrenExamined <- c(25, 15, 17,
                         1, 1, 6, 22,
                         NA, NA, NA, NA)
  ov16ElisaChildrenPositive <- c(1, 1, 1,
                                 0, 0, 4, 6,
                                 NA, NA, NA, NA)
  ov16ElisaChildrenLB <- c(0, 0, 0,
                           0, 12.4, 17.1, 15.4,
                           NA, NA, NA, NA)
  ov16ElisaChildrenUB <- c(12.3, 21.0, 18.4,
                           0, 20.6, 47.5, 51.2,
                           NA, NA, NA, NA)
  
  df <- data.frame(river_basin=riverBasin, prefecture=prefecture, village=village, mf_pop=mfExamined,
                   mf_pos=mfPositive, ov16_pop_all_ages=ov16ElisaExaminedAllAges,
                   ov16_pos_all_ages=ov16ElisaPositive, ov16_pop_children=ov16ElisaChildrenExamined,
                   ov16_pos_children=ov16ElisaChildrenPositive,
                   ov16_all_ages_lb=ov16ElisaLB,
                   ov16_all_ages_ub=ov16ElisaUB,
                   ov16_children_lb=ov16ElisaChildrenLB,
                   ov16_children_ub=ov16ElisaChildrenUB)
  return(df)
}
```

### Setup and Explore Data

```{r init_act_data, timeit=TRUE}
togoMFData <- togoMF()

togoOv16Data <- togoOv16()

togoVillageData <- togoVillage()

groupedVillageData <- togoVillageData %>% group_by(river_basin, prefecture) %>% summarise(across(-c('village'), ~ sum(.x, na.rm=TRUE)), .groups='drop') %>% as.data.frame() %>%
  mutate(
    mf_prev = mf_pos/mf_pop,
    ov16_prev_all_ages = ov16_pos_all_ages/ov16_pop_all_ages,
    ov16_prev_children = ov16_pos_children/ov16_pop_children
  )

groupedVillageData$all_ages_lb <- c(44.1, 12.8, 9.2)
groupedVillageData$all_ages_ub <- c(54.5, 44.3, 17.6)
groupedVillageData$children_lb <- c(15.4, NA, 0)
groupedVillageData$children_ub <- c(51.2, NA, 11.2)
  
togoVillageData <- togoVillageData %>% mutate(
  mf_prev=mf_pos/mf_pop,
  ov16_prev_all_ages = ov16_pos_all_ages/ov16_pop_all_ages,
  ov16_prev_children = ov16_pos_children/ov16_pop_children
)
```

### Exploring Sensitivity and Specificity Distributions
Sensitivity and Specificity data pulled from a search of papers (see SI of Ramani et al. 2025). Using the data, we create a distribution to pull sens/spec from.
```{r}
fit_to_beta <- function(vals) {
  mu <- mean(vals, na.rm=TRUE)
  var <- var(vals, na.rm=TRUE)
  if (mu + var > 1) {
    max_var <- (mu * ( 1 - mu))
    max_err <- 0.9999
    t <- (max_var / (max_var * max_err)) - 1
  } else {
    t <- (mu * ( 1 - mu) / var) - 1
  }
  alpha <- mu * t
  beta <- (1-mu) * t
  return(list(
    dbeta(seq(0, 1, 0.0001), alpha, beta),
    alpha,
    beta
  ))
}

# sens and spec vals from the paper
sens <- c(81, 95, 84, 60, 71.4, 53, 78, 83, 82.5) / 100
spec <- c(75, 97, 71.1, 99.99, 99.99, 84.8, 55.7) / 100

beta_params_sens <- fit_to_beta(sens)
sens_scale <- (max(hist(sens, plot=FALSE, breaks = seq(0, 1, by = 0.025))$counts) / max(beta_params_sens[[1]]))
sens_plot <- ggplot() +
  geom_histogram(aes(x=sens * 100, color="sensitivity data count"), fill="white",  binwidth = 2.5, boundary=0) +
  geom_line(aes(x=seq(0, 100, 0.01), y=beta_params_sens[[1]], color="Beta Density using data")) +
  theme_bw() +
  scale_x_continuous("Sensitivity (%)", breaks=seq(50, 100, 5), limits=c(50, 100)) +
  ylab("Count/Density") +
  scale_color_manual("Color", values=c("sensitivity data count"="black", "Beta Density Fit"="red", "Beta Density using data"="darkgreen")) +
  ggtitle(bquote(
    alpha: ~ .(round(beta_params_sens[[2]], 2)) ~ 
    beta: ~ .(round(beta_params_sens[[3]], 2))
  )) +
  theme(
    panel.grid.minor = element_blank()
  )
sens_plot

beta_params_spec <- fit_to_beta(spec)
spec_plot <- ggplot() +
  geom_histogram(aes(x=spec*100, color="specificity data count"), fill="white", binwidth = 1, boundary=0) +
  geom_line(aes(x=seq(0, 100, 0.01), y=beta_params_spec[[1]], color="Beta Density using data")) +
  theme_bw() +
  scale_x_continuous("Specificity (%)", breaks=seq(50, 100, 5), limits=c(50, NA)) +
  scale_color_manual("Color", values=c("sensitivity data count"="black", "Beta Density Fit"="red", "Beta Density using data"="darkgreen")) +
  ylab("Count/Density") +
  ggtitle(bquote(
    alpha: ~ .(round(beta_params_spec[[2]], 2)) ~ 
    beta: ~ .(round(beta_params_spec[[3]], 2))
  )) +
  theme(
    panel.grid.minor = element_blank()
  )
spec_plot

sens_spec_plot <- (sens_plot | spec_plot) + 
  plot_layout(guides = "collect") & theme(legend.position = "bottom")
sens_spec_plot
ggsave(paste0("images/images_", run_version,"/togo_sens_spec_dists.svg"), sens_spec_plot, width=6000, height=3600, units="px", dpi=600)

pull_from_beta <- function(params, n=1) {
  return(
    rbeta(n, params[[2]], params[[3]])
  )
}


calc_mean_ci <- function(params, n) {
  vals <- pull_from_beta(params, n)
  mean_val <- mean(vals)
  median_val <- median(vals)
  sample_varience = var(vals)
  se = sqrt(sample_varience / n)
  lower_bound = mean_val - 1.96 * se
  upper_bound = mean_val + 1.96 * se
  lower_ui = quantile(vals, 0.025)[[1]]
  upper_ui = quantile(vals, 0.975)[[1]]
  list(
    mean_val,
    lower_bound,
    upper_bound,
    median_val,
    lower_ui,
    upper_ui
  )
}

calc_mean_ci(beta_params_sens, 1500)
calc_mean_ci(beta_params_spec, 1500)
```

## Simulation Data

```{r simulation_processing_functions}
calcSensSpecSeroPrev <- function(run_seropos_data, sens=1, spec=1, prob=c()) {
  # Trust that the input is correct so we can vectorize the function
  sens <- sens[1]
  spec <- spec[1]
  
  new_seropos_data <- as.numeric(
    (run_seropos_data == 1 & prob <= sens) |
    (run_seropos_data == 0 & prob > spec)
  )
  
  return(new_seropos_data)
}

summarizeSimulationDataHelper <- function(data, index, sensSpec, groupByCols1, hypNamesLoc, hypothesisNames, extra_summary) {
  sens_val = sensSpec[1]
  spec_val = sensSpec[2]
  if (!("sens" %in% names(data)) | extra_summary) {
    data[, `:=`(
        sens = sens_val,
        spec = spec_val
    )]
  }
  
  tmp <- data[, .(
      age_groups,
      vctr.ctrl.eff,
      ov16_pos=calcSensSpecSeroPrev(ov16_pos, sens, spec, probs),
      ov16_pos_l3=calcSensSpecSeroPrev(ov16_pos_l3, sens, spec, probs),
      ov16_pos_l4=calcSensSpecSeroPrev(ov16_pos_l4, sens, spec, probs),
      ov16_pos_mating_no_mf=calcSensSpecSeroPrev(ov16_pos_mating_no_mf, sens, spec, probs),
      ov16_pos_mating_detectable_mf=calcSensSpecSeroPrev(ov16_pos_mating_detectable_mf, sens, spec, probs),
      ov16_pos_mating_any_mf=calcSensSpecSeroPrev(ov16_pos_mating_any_mf, sens, spec, probs),
      mf_prev
    ), by = c("run_num", "sens", "spec")
  ]
  
  tmp_summary <- tmp[, .(
      ov16_any_worm_prev = mean(ov16_pos),
      ov16_l3_prev = mean(ov16_pos_l3),
      ov16_l4_prev = mean(ov16_pos_l4),
      ov16_mating_no_mf_prev = mean(ov16_pos_mating_no_mf),
      ov16_mating_any_mf_prev = mean(ov16_pos_mating_any_mf),
      ov16_mating_detectable_mf_prev= mean(ov16_pos_mating_detectable_mf),
      num_mf_pos = sum(mf_prev),
      total_mf = .N,
      mf_prev = mean(mf_prev)
    ), by = groupByCols1
  ]
  if (extra_summary) {
    tmp_summary <- tmp_summary[, .(
        ov16_any_worm_prev = mean(ov16_any_worm_prev),
        ov16_l3_prev = mean(ov16_l3_prev),
        ov16_l4_prev = mean(ov16_l4_prev),
        ov16_mating_no_mf_prev = mean(ov16_mating_no_mf_prev),
        ov16_mating_any_mf_prev = mean(ov16_mating_any_mf_prev),
        ov16_mating_detectable_mf_prev= mean(ov16_mating_detectable_mf_prev),
        num_mf_pos = ceiling(mean(num_mf_pos)),
        total_mf = ceiling(mean(total_mf)),
        mf_prev = mean(mf_prev)
      ), by = c(groupByCols1[groupByCols1 != "run_num"])
    ]
    tmp_summary[, run_num := index]
    setcolorder(tmp_summary, c("run_num", setdiff(names(tmp_summary), "run_num")))
  }
  setcolorder(tmp, c(groupByCols1, setdiff(names(tmp), groupByCols1)))
  setnames(tmp_summary, old = names(tmp_summary)[hypNamesLoc], new = hypothesisNames)
  
  return(
    tmp_summary[, c(
      ..groupByCols1,
      "Mating worm pair with any mf",
      "num_mf_pos",
      "total_mf",
      "mf_prev"
    )]
  )
}

summarizeSimulationDataHelper_2 <- function(df, groupByCols1, groupByCols2, hypNamesLoc, hypothesisNames, groupHyp) {

  if("age_groups" %in% groupByCols2) {
    # df <- df1
    df <- df %>% dplyr::group_by(!!!syms(groupByCols2)) %>%
      dplyr::summarise(
        ov16_q1=quantile(ov16_prev, probs=0.025),
        ov16_q3=quantile(ov16_prev, probs=0.975),
        ov16_prev=mean(ov16_prev),
        mf_q1=quantile(mf_prev, probs=0.025),
        mf_q3=quantile(mf_prev, probs=0.975),
        mf_prev=mean(mf_prev),
        mf_lb=wilson.ci(mean(num_mf_pos), mean(total_mf))[1],
        mf_ub=wilson.ci(mean(num_mf_pos), mean(total_mf))[2],
        sens_mean = mean(sens),
        sens_lower = quantile(sens, probs=0.025),
        sens_upper = quantile(sens, probs=0.975),
        spec_mean = mean(spec),
        spec_lower = quantile(spec, probs=0.025),
        spec_upper = quantile(spec, probs=0.975),
        .groups="drop") %>% as.data.frame() %>%
      mutate(
        mf_prev = case_when(
          age_groups == 0 & mf_prev > 0 ~ 0,
          TRUE ~ mf_prev
        )
      )
  } else {
    df <- df %>% dplyr::group_by(!!!syms(groupByCols2)) %>%
    dplyr::summarise(
      ov16_prev_lb=quantile(ov16_prev, probs=0.025), #q1
      ov16_prev_ub=quantile(ov16_prev, probs=0.975), #q3
      ov16_prev=mean(ov16_prev),
      mf_q1=quantile(mf_prev, probs=0.025),
      mf_q3=quantile(mf_prev, probs=0.975),
      mf_prev=mean(mf_prev), 
      sens_mean = mean(sens),
      sens_lower = quantile(sens, probs=0.025),
      sens_upper = quantile(sens, probs=0.975),
      spec_mean = mean(spec),
      spec_lower = quantile(spec, probs=0.025),
      spec_upper = quantile(spec, probs=0.975),
      .groups="drop"
    ) %>% as.data.frame()
  }
  return(df)
}

summarizeSimulationData <- function(data, sensSpec=c(1,1), groupBySex=TRUE, sensAgeGroup=5, summary=FALSE, swapAgeGroups=TRUE, groupHyp=TRUE) {
  hypothesisNames <- c("Any worm", "L3 exposure", "L4-L5 moult", "Mating worm pair", "Mating worm pair with detectable mf", "Mating worm pair with any mf")
  groupByCols1 <- c("run_num", "age_groups", "vctr.ctrl.eff", "sens", "spec")
  groupByCols2 <- c("age_groups", "vctr.ctrl.eff", "Hypothesis")
  hypNamesLoc <- 6:11
  if(groupBySex) {
    groupByCols1 <- c("run_num", "age_groups", "sex", "vctr.ctrl.eff", "sens", "spec")
    groupByCols2 <- c("age_groups", "sex", "Hypothesis", "vctr.ctrl.eff")
    hypNamesLoc <- 7:12
  }
  if(summary) {
    groupByCols1 <- c("run_num", "vctr.ctrl.eff", "sens", "spec")
    groupByCols2 <- c("vctr.ctrl.eff", "Hypothesis")
    hypNamesLoc <- 5:10
  }
  if(swapAgeGroups) {
    # tmp <- data$age_groups
    data$age_groups <- data$age_groups_old #df$age_groups_lsr
    #df$age_groups_old  <- tmp
  }
  if (typeof(sensSpec) == "double") {
    sensSpec = list(sensSpec)
  }
  
  all_data <- vector("list", length(sensSpec))
  if (summary) {
    all_data_children <- vector("list", length(sensSpec))
  }
  
  data$probs <- runif(dim(data)[1])
  setDT(data)
  for (index in seq_along(sensSpec)) {
    # df <- summarizeSimulationDataHelper(df, sensSpec, sensAgeGroup)
    t0 <- proc.time()[3]
    sens_spec = sensSpec[[index]]
    all_data[[index]] <- summarizeSimulationDataHelper(
      data, index, sens_spec, groupByCols1,
      hypNamesLoc, hypothesisNames, extra_summary=length(sensSpec) > 1
    )
    if (summary) {
      all_data_children[[index]] <- summarizeSimulationDataHelper(
        data[(age >= 5) & (age < 11)], index, sens_spec,
        groupByCols1, hypNamesLoc, hypothesisNames,
        extra_summary=length(sensSpec) > 1
      )
    }
    t1 <- proc.time()[3]
    cat(
      sprintf(
        "Iteration %d (%f, %f) took %.3f seconds. Extra Summary: %d\n", index, sens_spec[1], sens_spec[2], t1 - t0, length(sensSpec) > 1
      )
    )
  }
  
  all_df <- rbindlist(all_data)
  
  df <- as.data.frame(melt(
    all_df,
    id.vars = c(groupByCols1, "mf_prev", "num_mf_pos", "total_mf"),
    measure.vars = hypothesisNames[length(hypothesisNames)],
    variable.name = "Hypothesis",
    value.name = "ov16_prev"
  ))
  df$Hypothesis <- as.character(df$Hypothesis)
  
  justChildren <- NA
  if(summary) {
    underTenDf <- as.data.frame(melt(
      rbindlist(all_data_children),
      id.vars = c(groupByCols1, "mf_prev", "num_mf_pos", "total_mf"),
      measure.vars = hypothesisNames[length(hypothesisNames)],
      variable.name = "Hypothesis",
      value.name = "ov16_prev"
    ))
    underTenDf$Hypothesis <- as.character(underTenDf$Hypothesis)
    
    print(paste("Total number of children under 10", dim(underTenDf)[1]))
    justChildren <- summarizeSimulationDataHelper_2(underTenDf, groupByCols1, groupByCols2, hypNamesLoc, hypothesisNames, groupHyp & !summary)
  }
  
  df <- summarizeSimulationDataHelper_2(df, groupByCols1, groupByCols2, hypNamesLoc, hypothesisNames, groupHyp & !summary)
  
  if(summary) {
    returnVals <- list(df, justChildren)
    names(returnVals) <- c("all_ages", "under10")
    return(returnVals)
  }
  return(df)
}

selectRunsFromAllPrefectures <- function(df1, df2, df3, sampleNum=c(), originalData=list()) {
  age_groups <- c(7.5, 13, 18, 23, 28, 33, 38, 43, 48, 53, 58, 70.5)
  sampleSize = c(172, 212, 95, 118, 195, 135, 105, 89, 90, 62, 61, 80)
  sampleSizeList = list()
  for(i in 1:length(age_groups)) {
    sampleSizeList[[age_groups[i]]] = sampleSize[i]
  }
  if(length(sampleNum) == 3) {
    df1 <- df1 %>% group_by(run_num) %>% slice_sample(n=sampleNum[1], replace=TRUE) %>% ungroup()
    df2 <- df2 %>% group_by(run_num) %>% slice_sample(n=sampleNum[2], replace=TRUE) %>% ungroup()
    df3 <- df3 %>% group_by(run_num) %>% slice_sample(n=sampleNum[3], replace=TRUE) %>% ungroup()
  }
  df1 <- df1 %>% mutate(prefecture="Oti/Kpendjal") %>% mutate(run_num = dense_rank(run_num))
  df2 <- df2 %>% mutate(prefecture="Keran") %>% mutate(run_num = dense_rank(run_num))
  df3 <- df3 %>%  mutate(prefecture="Bassar") %>% mutate(run_num = dense_rank(run_num))
  df <- base::rbind(
    df1, df2, df3
  )
  return_df <- df
  if(length(originalData) > 1) {
    return_df <- return_df %>% 
      mutate(age_groups_lsr = case_when(
        age < 1 ~ 0,
        age < 5 ~ 2.5,
        age < 11 ~ 7.5,
        age < 16 ~ 13,
        age < 21 ~ 18,
        age < 26 ~ 23,
        age < 31 ~ 28,
        age < 36 ~ 33,
        age < 41 ~ 38,
        age < 46 ~ 43,
        age < 51 ~ 48,
        age < 56 ~ 53,
        age < 61 ~ 58,
        TRUE ~ 70.5
      )) %>% 
      filter(age_groups_lsr > 2.5) %>%
      left_join(
        originalData %>% select(age_groups, total_pop), by=c("age_groups_lsr"="age_groups")
        ) %>%
      group_by(age_groups_lsr, ABR, Ke, run_num) %>%
      do(sample_n(., .$total_pop[1], replace = TRUE)) %>%
      ungroup()
  }
  return(return_df)
}

togo_sens_spec_vec <- c(0.714, 0.711)

sens<-c(81, 95, 78, 97, 84, 60, 80, 71.4, 53, 78, 83, 82.5)
print("Sens Vals")
print(quantile(sens, probs=c(0.25, 0.50, 0.75)))
print(mean(sens))
sens_range <- c(0.70, 0.80, 0.85)

spec<-c(94,75,97,71.1,100,84.8,55.7)
print("Spec Vals")
print(quantile(spec, probs=c(0.25, 0.50, 0.75)))
print(mean(spec))
spec_range <- c(0.70, 0.85, 0.95)
sens_spec_options <- list()
sens_spec_index <- 1
for(sens in sens_range) {
  for (spec in spec_range) {
    sens_spec_options[[sens_spec_index]] <- c(sens, spec)
    sens_spec_index <- sens_spec_index + 1
  }
}
sens_spec_options_2 <- sens_spec_options
sens_spec_options_2[[10]] <- c(-1, -1)
```

### Setup and Explore Simulation Data

#### Checking Projected MFP
```{r}
look_at_mfp = FALSE
look_at_time_trends = FALSE
all_places_to_pick <- c("_start_2015") # , "_mid_2015", "_end_2015")
if (look_at_mfp) {
  if (look_at_time_trends) {
    togo_mf_trend <- rbind(
      readRDS(paste0("data/bassar", folder, "togo_bassar_mfp_trends_data.RDS"))$mf_prev_df %>% group_by(Ke, run_num, vctr.ctrl.eff) %>% mutate(prefecture="bassar", time = (row_number()/2)) %>% ungroup(), 
      readRDS(paste0("data/oti", folder, "togo_oti_mfp_trends_data.RDS"))$mf_prev_df %>% group_by(Ke, run_num, vctr.ctrl.eff) %>% mutate(prefecture="oti/kpendjal", time = (row_number()/2)) %>% ungroup(),
      readRDS(paste0("data/keran", folder, "togo_keran_mfp_trends_data.RDS"))$mf_prev_df %>% group_by(Ke, run_num, vctr.ctrl.eff) %>% mutate(prefecture="keran", time = (row_number()/2)) %>% ungroup()
    )
    
    if (use_oti_100) {
      togo_mf_trend <- rbind(
        togo_mf_trend,
        readRDS(paste0("data/oti", oti_folder_100, "togo_oti_mfp_trends_data.RDS"))$mf_prev_df %>% group_by(Ke, run_num, vctr.ctrl.eff) %>% mutate(prefecture="oti/kpendjal_vc_100", time = (row_number()/2)) %>% ungroup()
      )
    }
    
    togo_mf_trend <- togo_mf_trend %>% filter(time < 220) %>% group_by(prefecture, vctr.ctrl.eff, time, Ke) %>% summarize(prev=mean(mf_prev), .groups="drop") %>% mutate(prev_type="MF Prevalence", sero="no serorevert")
    
    unpack_sero_trends <- function(file, prefecture) {
      no_reversion <- as.data.frame(readRDS(file)$ov16_trend_df) %>% group_by(Ke, run_num, vctr.ctrl.eff) %>% mutate(time = (row_number()/2), prefecture=prefecture) %>% ungroup() %>% mutate(prev_type="Ov16 Seroprevalence", sero="no serorevert")
      with_reversion <- as.data.frame(readRDS(file)$ov16_serorevert_trend_df) %>% group_by(Ke, run_num, vctr.ctrl.eff) %>% mutate(time = (row_number()/2), prefecture=prefecture) %>% ungroup() %>% mutate(prev_type="Ov16 Seroprevalence", sero="serorevert")
      return(rbind(no_reversion, with_reversion))
    }
    
    togo_bassar_sero_trend <- unpack_sero_trends(paste0("data/bassar", folder, "togo_bassar_ov16_trends.RDS"), "Bassar")
    togo_oti_sero_trend <- unpack_sero_trends(paste0("data/oti", folder, "togo_oti_ov16_trends.RDS"), "oti/kpendjal")
    togo_keran_sero_trend <- unpack_sero_trends(paste0("data/keran", folder, "togo_keran_ov16_trends.RDS"), "Keran")
    togo_sero_trend <- rbind(togo_bassar_sero_trend, togo_oti_sero_trend, togo_keran_sero_trend)
    
    if (use_oti_100) {
      togo_sero_trend <- rbind(
        togo_sero_trend,
        unpack_sero_trends(paste0("data/oti", oti_folder_100, "togo_oti_ov16_trends.RDS"), "oti/kpendjal_vc_100")
      )
    }
    
    togo_sero_trend <- togo_sero_trend %>% filter(time < 220) %>% group_by(prefecture, vctr.ctrl.eff, time, Ke, prev_type, sero) %>% summarize(prev=mean(ov16_vals), .groups="drop") %>% mutate(prefecture = tolower(prefecture))
    
    togo_time_trends <- rbind(togo_sero_trend, togo_mf_trend)
    
    time_trend_plot_full <- ggplot() + 
      geom_line(data=togo_time_trends %>% filter(time %% 1 == 0 & vctr.ctrl.eff <= 1) %>% mutate(vctr.ctrl.eff = factor(vctr.ctrl.eff)), aes(x=time, y=prev*100, color=vctr.ctrl.eff, linetype=sero)) +
      facet_grid(factor(Ke) + prev_type~prefecture) +
      theme_bw() +
      scale_x_continuous("Time (years)", limits=c(175, NA), breaks=c(180, seq(189, 220, 10), 219), labels=c(1976, seq(1985, 2016, 10), 2015)) +
      ylab("Prevalence (%)") +
      scale_color_manual("Vector Control Efficacy", values=c("brown", "red", "orange", "#008080"), labels=c("60%", "75%", "90%", "100%")) +
      guides(linetype="none") +
      theme(
          plot.title = element_text(size=10, hjust = 0.5),
          axis.title.y = element_text(size=10),
          title = element_text(size=10),
          legend.text = element_text(size=6),
          legend.title = element_text(size=8),
          legend.key.size = unit(0.8, 'lines'),
          legend.position = "bottom",  # Set legend to the bottom
          legend.direction = "horizontal",
          axis.text.y = element_text(size=6),
          axis.text.x = element_text(size=6),
          strip.placement = "outside",
          panel.grid.minor = element_blank(),
          axis.line.x = element_line(color = "black"),
          axis.line.y = element_line(color = "black"),
          strip.text.y = element_text(angle=0),
          axis.line.y.right = element_blank()
        )
    time_trend_plot_full
    ggsave(paste0("images/images_", run_version, "/togo_time_trend_all.png"), time_trend_plot_full, width=4250, height=3000, units="px", dpi=450)
    
    time_trend_plot <- ggplot() + 
      geom_line(data=togo_time_trends %>% filter(Ke == 0.3, time %% 1 == 0 & vctr.ctrl.eff < 1) %>% filter(
        (prefecture=="keran" & vctr.ctrl.eff == 0.90) |
        (prefecture=="bassar" & vctr.ctrl.eff == 0.60) |
        (prefecture=="oti/kpendjal" & vctr.ctrl.eff == 0.75) |
        (prefecture=="oti/kpendjal_vc_100" & vctr.ctrl.eff == 1)
      ) %>% mutate(vctr.ctrl.eff = factor(vctr.ctrl.eff)), aes(x=time, y=prev*100, color=vctr.ctrl.eff, linetype=sero)) +
      facet_grid(prefecture~prev_type) +
      theme_bw() +
      scale_x_continuous("Time (years)", limits=c(175, NA), breaks=c(180, seq(189, 220, 10), 219), labels=c(1976, seq(1985, 2016, 10), 2015)) +
      ylab("Prevalence (%)") +
      scale_color_manual("Vector Control Efficacy", values=c("brown", "red", "orange", "#008080"), labels=c("60%", "75%", "90%", "100%")) +
      guides(linetype="none", color="none") +
      theme(
          plot.title = element_text(size=10, hjust = 0.5),
          axis.title.y = element_text(size=10),
          title = element_text(size=10),
          legend.text = element_text(size=6),
          legend.title = element_text(size=8),
          legend.key.size = unit(0.8, 'lines'),
          legend.position = "bottom",  # Set legend to the bottom
          legend.direction = "horizontal",
          axis.text.y = element_text(size=6),
          axis.text.x = element_text(size=6),
          strip.background = element_blank(),
          strip.placement = "outside",
          panel.grid.minor = element_blank(),
          axis.line.x = element_line(color = "black"),
          axis.line.y = element_line(color = "black"),
          strip.text.y = element_text(angle=0),
          axis.line.y.right = element_blank()
        )
    time_trend_plot
    ggsave(paste0("images/images_", run_version, "/togo_time_trend_k3.png"), time_trend_plot, width=4250, height=3000, units="px", dpi=450)
  }
  
  all_mfp_df <- data.frame(matrix(ncol=9, nrow=0))
  colnames(all_mfp_df) <- c("sample_point", "prefecture", "vctr.ctrl.eff", "Ke", "mf_prev", "lb", "ub", "q1", "q3")
  for(prefecture in c("bassar", "oti", "keran", "oti_100_vc")) {
    for(pick in all_places_to_pick) {
      print(paste(prefecture, pick))
      folder_to_use = folder
      prefecture_to_use = str_replace(prefecture, "oti", "oti/kpendjal")
      prefecture_folder = prefecture
      if (prefecture == "oti_100_vc") {
        if (!use_oti_100) {
          next
        }
        prefecture_folder = "oti"
        folder_to_use = oti_folder_100
      }
      tmp <- readRDS(paste("data/", prefecture_folder, folder_to_use, "togo_", prefecture_folder, "_100_mount_data", pick, ".RDS", sep=""))$allOutputs %>% 
        mutate(age_groups_lsr = case_when(
          age < 1 ~ 0,
          age < 5 ~ 2.5,
          age < 11 ~ 7.5,
          age < 16 ~ 13,
          age < 21 ~ 18,
          age < 26 ~ 23,
          age < 31 ~ 28,
          age < 36 ~ 33,
          age < 41 ~ 38,
          age < 46 ~ 43,
          age < 51 ~ 48,
          age < 56 ~ 53,
          age < 61 ~ 58,
          TRUE ~ 70.5
        )) %>% 
        filter(age_groups_lsr > 2.5) %>%
        left_join(
          togoMFData %>% select(age_groups, total_pop), by=c("age_groups_lsr"="age_groups")
          ) %>%
        group_by(age_groups_lsr, ABR, Ke, run_num) %>%
        do(sample_n(., .$total_pop[1], replace = TRUE)) %>%
        ungroup()
      tmp <- tmp %>% filter(age >= 5) %>%
        group_by(run_num, vctr.ctrl.eff, Ke) %>% 
        summarize(num_pos = sum(mf_prev), total=n(), mf_prev=mean(mf_prev), .groups="drop") %>% 
        group_by(vctr.ctrl.eff, Ke) %>% 
        summarize(
          q1 = quantile(mf_prev, probs=0.025)*100,
          q3 = quantile(mf_prev, probs=0.975)*100,
          mf_prev = mean(mf_prev)*100, 
          lb=wilson.ci(mean(num_pos), mean(total))[1]*100, 
          ub=wilson.ci(mean(num_pos), mean(total))[2]*100, .groups="drop") %>% 
        mutate(prefecture=prefecture_to_use, sample_point=pick) %>% 
        select(sample_point, prefecture, everything()) %>% 
        mutate(lb=ifelse(lb < 0, 0, lb))
      all_mfp_df <- rbind(all_mfp_df, tmp)
      rm(tmp)
    }
  }
  
  process_combined_mfp <- function(data, name="combined") {
    return(data %>% filter(age >= 5) %>%
      group_by(run_num, vctr.ctrl.eff, Ke) %>% 
      summarize(num_pos = sum(mf_prev), total=n(), mf_prev=mean(mf_prev), .groups="drop") %>% 
      group_by(vctr.ctrl.eff, Ke) %>% 
      summarize(
        q1 = quantile(mf_prev, probs=0.025)*100,
        q3 = quantile(mf_prev, probs=0.975)*100,
        mf_prev = mean(mf_prev)*100,
        lb=wilson.ci(mean(num_pos), mean(total))[1]*100, 
        ub=wilson.ci(mean(num_pos), mean(total))[2]*100, .groups="drop") %>%
      mutate(prefecture=name, sample_point=pick) %>% 
      select(sample_point, prefecture, everything()) %>% 
      mutate(lb=ifelse(lb < 0, 0, lb))
    )
  }
  
  for(pick in all_places_to_pick) {
    combined_mfp <- selectRunsFromAllPrefectures(
      readRDS(paste("data/oti", folder, "togo_oti_100_mount_data", pick, ".RDS", sep=""))$allOutputs,
      readRDS(paste("data/keran", folder, "togo_keran_100_mount_data", pick, ".RDS", sep=""))$allOutputs,
      readRDS(paste("data/bassar", folder, "togo_bassar_100_mount_data", pick, ".RDS", sep=""))$allOutputs,
      sampleNum=c(500*0.22,500*0.37,500*0.41),
      togoMFData
      ) %>% process_combined_mfp()
    combined_mfp_best_fit <- selectRunsFromAllPrefectures(
      readRDS(paste("data/oti", folder, "togo_oti_100_mount_data", pick, ".RDS", sep=""))$allOutputs %>% filter(vctr.ctrl.eff == 0.75) %>% mutate(run_num = run_num - 1500, vctr.ctrl.eff=-1),
      readRDS(paste("data/keran", folder, "togo_keran_100_mount_data", pick, ".RDS", sep=""))$allOutputs %>% filter(vctr.ctrl.eff == 0.90) %>% mutate(run_num = run_num - 2, vctr.ctrl.eff=-1),
      readRDS(paste("data/bassar", folder, "togo_bassar_100_mount_data", pick, ".RDS", sep=""))$allOutputs %>% filter(vctr.ctrl.eff == 0.60) %>% mutate(vctr.ctrl.eff=-1),
      sampleNum=c(500*0.22,500*0.37,500*0.41),
      togoMFData
      ) %>% process_combined_mfp()
    all_mfp_df <- rbind(all_mfp_df, combined_mfp, combined_mfp_best_fit)
    rm(combined_mfp)
    rm(combined_mfp_best_fit)
    if (use_oti_100) {
      combined_mfp_vc_100 <- selectRunsFromAllPrefectures(
        readRDS(paste("data/oti", oti_folder_100, "togo_oti_100_mount_data", pick, ".RDS", sep=""))$allOutputs,
        readRDS(paste("data/keran", folder, "togo_keran_100_mount_data", pick, ".RDS", sep=""))$allOutputs %>% mutate(vctr.ctrl.eff=ifelse(vctr.ctrl.eff == 0.9, 1, vctr.ctrl.eff)) %>% filter(vctr.ctrl.eff == 1),
        readRDS(paste("data/bassar", folder, "togo_bassar_100_mount_data", pick, ".RDS", sep=""))$allOutputs %>% mutate(vctr.ctrl.eff=ifelse(vctr.ctrl.eff == 0.9, 1, vctr.ctrl.eff)) %>% filter(vctr.ctrl.eff == 1),
        sampleNum=c(500*0.22,500*0.37,500*0.41),
        togoMFData
        ) %>% process_combined_mfp(name="combined_oti_vc_100")
      all_mfp_df <- rbind(all_mfp_df, combined_mfp_vc_100)
      rm(combined_mfp_vc_100)
    }
  }
  
  calc_sig_figs <- function(x, sig=2) {
    return(ifelse(x == 0, "0.00", as.integer(x) + signif(x - as.integer(x), sig)))
  }
  
  kable_all_mfp_df <- all_mfp_df %>% 
    pivot_wider(id_cols=c(sample_point, prefecture, vctr.ctrl.eff), names_from=Ke, values_from=c(mf_prev, q1, q3)) %>%
    mutate(
      k3_vals = paste0(calc_sig_figs(mf_prev_0.3), "% (", calc_sig_figs(q1_0.3), "%-", calc_sig_figs(q3_0.3), "%)"),
      k4_vals = paste0(calc_sig_figs(mf_prev_0.4), "% (", calc_sig_figs(q1_0.4), "%-", calc_sig_figs(q3_0.4), "%)"),
      prefecture = factor(prefecture, levels=c("oti/kpendjal", "oti/kpendjal_100_vc", "keran", "bassar", "combined", "combined_oti_vc_100")),
      sample_point = factor(sample_point, levels=c("_end_2015", "_mid_2015", "_start_2015"))
    ) %>%
    select(sample_point, prefecture, vctr.ctrl.eff, k3_vals, k4_vals) %>%
    arrange(sample_point, prefecture, vctr.ctrl.eff)
  kable_all_mfp_df %>% kable('html', escape=FALSE) %>% kable_classic()
  kable_all_mfp_df %>% write.csv(paste0("images/images_", run_version, "/mfp_tuning.csv"), row.names=FALSE)
}
```


### New Runs Aggregation
#### 100 Mount
```{r}
sample_num_ov16 = c(500*0.394,500*0.552,500*0.054)
fix_age_groups <- function(df) {
  return(df %>% mutate(
    age_groups = case_when(
      age <= 30 ~ ceiling(age/1)*1,
      age <= 75 ~ ceiling(age/5)*5,
      TRUE ~ 80
    ),
    age_groups_old = case_when(
            age < 1 ~ 0,
            age < 5 ~ 2.5,
            age < 11 ~ 7.5,
            age < 16 ~ 13,
            age < 21 ~ 18,
            age < 26 ~ 23,
            age < 31 ~ 28,
            age < 36 ~ 33,
            age < 41 ~ 38,
            age < 46 ~ 43,
            age < 51 ~ 48,
            age < 56 ~ 53,
            age < 61 ~ 58,
            age < 66 ~ 63,
            TRUE ~ 73
          ),
    age_groups_lsr = case_when(
          age < 11 ~ 7.5,
          age < 16 ~ 13,
          age < 21 ~ 18,
          age < 26 ~ 23,
          age < 31 ~ 28,
          age < 36 ~ 33,
          age < 41 ~ 38,
          age < 46 ~ 48,
          age < 51 ~ 53,
          age < 56 ~ 58,
          age < 61 ~ 63,
          TRUE ~ 73
      )
    ))
}
place_to_pick = "_start_2015"
k3_100_mount_simulation_summary_combined_sens_spec_list <- list()

togo_bassar_100_mount_agg <- readRDS(paste("data/bassar", folder, "togo_bassar_100_mount_data", place_to_pick, ".RDS", sep=""))
simulatedBassar_k3_100_mount <- togo_bassar_100_mount_agg$allOutputs %>% filter(Ke == 0.3) %>% fix_age_groups()
for (sens_spec_val in sens_spec_options) {
  k3_100_mount_simulation_summary_combined_sens_spec_list[[paste("bassar", sens_spec_val, collapse="_")]] <- summarizeSimulationData(simulatedBassar_k3_100_mount %>% mutate(sens = sens_spec_val[1], spec=sens_spec_val[2]), sens_spec_val, groupBySex=FALSE, summary=TRUE)
}

togo_oti_100_mount_agg <- readRDS(paste("data/oti", folder, "togo_oti_100_mount_data", place_to_pick, ".RDS", sep=""))
simulatedOti_k3_100_mount <- togo_oti_100_mount_agg$allOutputs %>% filter(Ke == 0.3) %>% fix_age_groups()

if (use_oti_100) {
  togo_oti_100_mount_agg_vc_100 <- readRDS(paste("data/oti", oti_folder_100, "togo_oti_100_mount_data", place_to_pick, ".RDS", sep=""))
  simulatedOti_k3_100_mount_vc_100 <- togo_oti_100_mount_agg_vc_100$allOutputs %>% filter(Ke == 0.3) %>% fix_age_groups()
  simulatedOti_k3_100_mount[
    simulatedOti_k3_100_mount$vctr.ctrl.eff == 0.90,
  ] = simulatedOti_k3_100_mount_vc_100
  simulatedOti_k3_100_mount[
    simulatedOti_k3_100_mount$vctr.ctrl.eff == 1,
  "vctr.ctrl.eff"] = 0.90
}

for (sens_spec_val in sens_spec_options) {
  k3_100_mount_simulation_summary_combined_sens_spec_list[[paste("oti", sens_spec_val, collapse="_")]] <- summarizeSimulationData(simulatedOti_k3_100_mount %>% mutate(sens = sens_spec_val[1], spec=sens_spec_val[2]), sens_spec_val, groupBySex=FALSE, summary=TRUE)
}

togo_keran_100_mount_agg <- readRDS(paste("data/keran", folder, "togo_keran_100_mount_data", place_to_pick, ".RDS", sep=""))
simulatedKeran_k3_100_mount <- togo_keran_100_mount_agg$allOutputs %>% filter(Ke == 0.3) %>% fix_age_groups()
for (sens_spec_val in sens_spec_options) {
  k3_100_mount_simulation_summary_combined_sens_spec_list[[paste("keran", sens_spec_val, collapse="_")]] <- summarizeSimulationData(simulatedKeran_k3_100_mount %>% mutate(sens = sens_spec_val[1], spec=sens_spec_val[2]), sens_spec_val, groupBySex=FALSE, summary=TRUE)
}

k3_100_mount_simulation_summary_age_group_combined_sens_spec_list <- list()
combinedSimulation_k3_100_mount <- selectRunsFromAllPrefectures(
  simulatedOti_k3_100_mount,
  simulatedKeran_k3_100_mount,
  simulatedBassar_k3_100_mount,
  sampleNum=sample_num_ov16)
for (sens_spec_val in sens_spec_options) {
  k3_100_mount_simulation_summary_age_group_combined_sens_spec_list[[paste(sens_spec_val, collapse="_")]] <- summarizeSimulationData(combinedSimulation_k3_100_mount %>% mutate(sens = sens_spec_val[1], spec=sens_spec_val[2]), sens_spec_val, groupBySex=FALSE)
}

if(use_k4) {
  k4_100_mount_simulation_summary_combined_sens_spec_list <- list()

  simulatedBassar_k4_100_mount <- togo_bassar_100_mount_agg$allOutputs %>% filter(Ke == 0.4) %>% fix_age_groups()
  for (sens_spec_val in sens_spec_options) {
    k4_100_mount_simulation_summary_combined_sens_spec_list[[paste("bassar", sens_spec_val, collapse="_")]] <- summarizeSimulationData(simulatedBassar_k4_100_mount %>% mutate(sens = sens_spec_val[1], spec=sens_spec_val[2]), sens_spec_val, groupBySex=FALSE, summary=TRUE)
  }
  
  simulatedOti_k4_100_mount <- togo_oti_100_mount_agg$allOutputs %>% filter(Ke == 0.4) %>% fix_age_groups()
  for (sens_spec_val in sens_spec_options) {
    k4_100_mount_simulation_summary_combined_sens_spec_list[[paste("oti", sens_spec_val, collapse="_")]] <- summarizeSimulationData(simulatedOti_k4_100_mount %>% mutate(sens = sens_spec_val[1], spec=sens_spec_val[2]), sens_spec_val, groupBySex=FALSE, summary=TRUE)
  }
  
  simulatedKeran_k4_100_mount <- togo_keran_100_mount_agg$allOutputs %>% filter(Ke == 0.4) %>% fix_age_groups()
  for (sens_spec_val in sens_spec_options) {
    k4_100_mount_simulation_summary_combined_sens_spec_list[[paste("keran", sens_spec_val, collapse="_")]] <- summarizeSimulationData(simulatedKeran_k4_100_mount %>% mutate(sens = sens_spec_val[1], spec=sens_spec_val[2]), sens_spec_val, groupBySex=FALSE, summary=TRUE)
  }
  
  k4_100_mount_simulation_summary_age_group_combined_sens_spec_list <- list()
  combinedSimulation_k4_100_mount <- selectRunsFromAllPrefectures(
    simulatedOti_k4_100_mount,
    simulatedKeran_k4_100_mount,
    simulatedBassar_k4_100_mount,
    sampleNum=sample_num_ov16)
  
  for (sens_spec_val in sens_spec_options) {
    k4_100_mount_simulation_summary_age_group_combined_sens_spec_list[[paste(sens_spec_val, collapse="_")]] <- summarizeSimulationData(combinedSimulation_k4_100_mount %>% mutate(sens = sens_spec_val[1], spec=sens_spec_val[2]), sens_spec_val, groupBySex=FALSE)
}
}

if(use_oti_100) {
  rm(togo_oti_100_mount_agg_vc_100)
}
rm(togo_bassar_100_mount_agg)
rm(togo_oti_100_mount_agg)
rm(togo_keran_100_mount_agg)
```

#### Instant Seroreversion Aggregated
```{r}
k3_instant_seroreversion_simulation_summary_combined_sens_spec_list <- list()

togo_bassar_instant_seroreversion_agg <- readRDS(paste("data/bassar", folder, "togo_bassar_instant_seroreversion_data", place_to_pick, ".RDS", sep=""))
simulatedBassar_k3_instant_seroreversion <- togo_bassar_instant_seroreversion_agg$allOutputs %>% filter(Ke == 0.3) %>% fix_age_groups()

for (sens_spec_val in sens_spec_options) {
  k3_instant_seroreversion_simulation_summary_combined_sens_spec_list[[paste("bassar", sens_spec_val, collapse="_")]] <- summarizeSimulationData(simulatedBassar_k3_instant_seroreversion %>% mutate(sens = sens_spec_val[1], spec=sens_spec_val[2]), sens_spec_val, groupBySex=FALSE, summary=TRUE)
}

togo_oti_instant_seroreversion_agg <- readRDS(paste("data/oti", folder, "togo_oti_instant_seroreversion_data", place_to_pick, ".RDS", sep=""))
simulatedOti_k3_instant_seroreversion <- togo_oti_instant_seroreversion_agg$allOutputs %>% filter(Ke == 0.3) %>% fix_age_groups()
if (use_oti_100) {
  togo_oti_seroreversion_agg_vc_100 <- readRDS(paste("data/oti", oti_folder_100, "togo_oti_finite_seroreversion_data", place_to_pick, ".RDS", sep=""))
  simulatedOti_k3_instant_seroreversion_vc_100 <- togo_oti_seroreversion_agg_vc_100$allOutputs %>% filter(Ke == 0.3) %>% fix_age_groups()
  simulatedOti_k3_instant_seroreversion[
    simulatedOti_k3_instant_seroreversion$vctr.ctrl.eff == 0.90,
  ] = simulatedOti_k3_instant_seroreversion_vc_100
  simulatedOti_k3_instant_seroreversion[
    simulatedOti_k3_instant_seroreversion$vctr.ctrl.eff == 1,
  "vctr.ctrl.eff"] = 0.90
}
for (sens_spec_val in sens_spec_options) {
  k3_instant_seroreversion_simulation_summary_combined_sens_spec_list[[paste("oti", sens_spec_val, collapse="_")]] <- summarizeSimulationData(simulatedOti_k3_instant_seroreversion %>% mutate(sens = sens_spec_val[1], spec=sens_spec_val[2]), sens_spec_val, groupBySex=FALSE, summary=TRUE)
}

togo_keran_instant_seroreversion_agg <- readRDS(paste("data/keran", folder, "togo_keran_instant_seroreversion_data", place_to_pick, ".RDS", sep=""))
simulatedKeran_k3_instant_seroreversion <- togo_keran_instant_seroreversion_agg$allOutputs %>% filter(Ke == 0.3) %>% fix_age_groups()

for (sens_spec_val in sens_spec_options) {
  k3_instant_seroreversion_simulation_summary_combined_sens_spec_list[[paste("keran", sens_spec_val, collapse="_")]] <- summarizeSimulationData(simulatedKeran_k3_instant_seroreversion %>% mutate(sens = sens_spec_val[1], spec=sens_spec_val[2]), sens_spec_val, groupBySex=FALSE, summary=TRUE)
}


k3_instant_seroreversion_simulation_summary_age_group_combined_sens_spec_list <- list()
combinedSimulation_k3_instant_seroreversion <- selectRunsFromAllPrefectures(
  simulatedOti_k3_instant_seroreversion,
  simulatedKeran_k3_instant_seroreversion,
  simulatedBassar_k3_instant_seroreversion,
  sampleNum=sample_num_ov16)

for (sens_spec_val in sens_spec_options) {
  k3_instant_seroreversion_simulation_summary_age_group_combined_sens_spec_list[[paste(sens_spec_val, collapse="_")]] <- summarizeSimulationData(simulatedOti_k3_instant_seroreversion %>% mutate(sens = sens_spec_val[1], spec=sens_spec_val[2]), sens_spec_val, groupBySex=FALSE)
}

if(use_k4) {
  k4_instant_seroreversion_simulation_summary_combined_sens_spec_list <- list()
  
  simulatedBassar_k4_instant_seroreversion <- togo_bassar_instant_seroreversion_agg$allOutputs %>% filter(Ke == 0.4) %>% fix_age_groups()
  
  for (sens_spec_val in sens_spec_options) {
    k4_instant_seroreversion_simulation_summary_combined_sens_spec_list[[paste("bassar", sens_spec_val, collapse="_")]] <- summarizeSimulationData(simulatedBassar_k4_instant_seroreversion %>% mutate(sens = sens_spec_val[1], spec=sens_spec_val[2]), sens_spec_val, groupBySex=FALSE, summary=TRUE)
  }
  
  simulatedOti_k4_instant_seroreversion <- togo_oti_instant_seroreversion_agg$allOutputs %>% filter(Ke == 0.4) %>% fix_age_groups()
  if (use_oti_100) {
    togo_oti_seroreversion_agg_vc_100 <- readRDS(paste("data/oti", oti_folder_100, "togo_oti_instant_seroreversion_data", place_to_pick, ".RDS", sep=""))
    simulatedOti_k4_seroreversion_vc_100 <- togo_oti_seroreversion_agg_vc_100$allOutputs %>% filter(Ke == 0.3) %>% fix_age_groups()
    simulatedOti_k4_instant_seroreversion[
      simulatedOti_k4_instant_seroreversion$vctr.ctrl.eff == 0.90,
    ] = simulatedOti_k4_seroreversion_vc_100
    simulatedOti_k4_instant_seroreversion[
      simulatedOti_k4_instant_seroreversion$vctr.ctrl.eff == 1,
    "vctr.ctrl.eff"] = 0.90
  }
  for (sens_spec_val in sens_spec_options) {
    k4_instant_seroreversion_simulation_summary_combined_sens_spec_list[[paste("oti", sens_spec_val, collapse="_")]] <- summarizeSimulationData(simulatedOti_k4_instant_seroreversion %>% mutate(sens = sens_spec_val[1], spec=sens_spec_val[2]), sens_spec_val, groupBySex=FALSE, summary=TRUE)
  }
  
  simulatedKeran_k4_instant_seroreversion <- togo_keran_instant_seroreversion_agg$allOutputs %>% filter(Ke == 0.4) %>% fix_age_groups()
  
  for (sens_spec_val in sens_spec_options) {
    k4_instant_seroreversion_simulation_summary_combined_sens_spec_list[[paste("keran", sens_spec_val, collapse="_")]] <- summarizeSimulationData(simulatedKeran_k4_instant_seroreversion %>% mutate(sens = sens_spec_val[1], spec=sens_spec_val[2]), sens_spec_val, groupBySex=FALSE, summary=TRUE)
  }
  
  
  
  
  k4_instant_seroreversion_simulation_summary_age_group_combined_sens_spec_list <- list()
  combinedSimulation_k4_seroreversion <- selectRunsFromAllPrefectures(
    simulatedOti_k4_instant_seroreversion,
    simulatedKeran_k4_instant_seroreversion,
    simulatedBassar_k4_instant_seroreversion,
    sampleNum=sample_num_ov16)
  for (sens_spec_val in sens_spec_options) {
    k4_instant_seroreversion_simulation_summary_age_group_combined_sens_spec_list[[paste(sens_spec_val, collapse="_")]] <- summarizeSimulationData(combinedSimulation_k4_seroreversion %>% mutate(sens = sens_spec_val[1], spec=sens_spec_val[2]), sens_spec_val, groupBySex=FALSE)
  }
}

if(use_oti_100) {
  rm(togo_oti_seroreversion_agg_vc_100)
}
rm(togo_bassar_instant_seroreversion_agg)
rm(togo_oti_instant_seroreversion_agg)
rm(togo_keran_instant_seroreversion_agg)

```

#### Gradual Seroreversion Aggregated
```{r}
k3_gradual_seroreversion_simulation_summary_combined_sens_spec_list <- list()

togo_bassar_gradual_seroreversion_agg <- readRDS(paste("data/bassar", folder, "togo_bassar_finite_seroreversion_data", place_to_pick, ".RDS", sep=""))
simulatedBassar_k3_gradual_seroreversion <- togo_bassar_gradual_seroreversion_agg$allOutputs %>% filter(Ke == 0.3) %>% fix_age_groups()

for (sens_spec_val in sens_spec_options) {
  k3_gradual_seroreversion_simulation_summary_combined_sens_spec_list[[paste("bassar", sens_spec_val, collapse="_")]] <- summarizeSimulationData(simulatedBassar_k3_gradual_seroreversion %>% mutate(sens = sens_spec_val[1], spec=sens_spec_val[2]), sens_spec_val, groupBySex=FALSE, summary=TRUE)
}

togo_oti_gradual_seroreversion_agg <- readRDS(paste("data/oti", folder, "togo_oti_finite_seroreversion_data", place_to_pick, ".RDS", sep=""))
simulatedOti_k3_gradual_seroreversion <- togo_oti_gradual_seroreversion_agg$allOutputs %>% filter(Ke == 0.3) %>% fix_age_groups()
if (use_oti_100) {
  togo_oti_seroreversion_agg_vc_100 <- readRDS(paste("data/oti", oti_folder_100, "togo_oti_finite_seroreversion_data", place_to_pick, ".RDS", sep=""))
  simulatedOti_k3_gradual_seroreversion_vc_100 <- togo_oti_seroreversion_agg_vc_100$allOutputs %>% filter(Ke == 0.3) %>% fix_age_groups()
  simulatedOti_k3_gradual_seroreversion[
    simulatedOti_k3_gradual_seroreversion$vctr.ctrl.eff == 0.90,
  ] = simulatedOti_k3_gradual_seroreversion_vc_100
  simulatedOti_k3_gradual_seroreversion[
    simulatedOti_k3_gradual_seroreversion$vctr.ctrl.eff == 1,
  "vctr.ctrl.eff"] = 0.90
}
for (sens_spec_val in sens_spec_options) {
  k3_gradual_seroreversion_simulation_summary_combined_sens_spec_list[[paste("oti", sens_spec_val, collapse="_")]] <- summarizeSimulationData(simulatedOti_k3_gradual_seroreversion %>% mutate(sens = sens_spec_val[1], spec=sens_spec_val[2]), sens_spec_val, groupBySex=FALSE, summary=TRUE)
}

togo_keran_gradual_seroreversion_agg <- readRDS(paste("data/keran", folder, "togo_keran_finite_seroreversion_data", place_to_pick, ".RDS", sep=""))
simulatedKeran_k3_gradual_seroreversion <- togo_keran_gradual_seroreversion_agg$allOutputs %>% filter(Ke == 0.3) %>% fix_age_groups()

for (sens_spec_val in sens_spec_options) {
  k3_gradual_seroreversion_simulation_summary_combined_sens_spec_list[[paste("keran", sens_spec_val, collapse="_")]] <- summarizeSimulationData(simulatedKeran_k3_gradual_seroreversion %>% mutate(sens = sens_spec_val[1], spec=sens_spec_val[2]), sens_spec_val, groupBySex=FALSE, summary=TRUE)
}


k3_gradual_seroreversion_simulation_summary_age_group_combined_sens_spec_list <- list()
combinedSimulation_k3_finite_seroreversion <- selectRunsFromAllPrefectures(
  simulatedOti_k3_gradual_seroreversion,
  simulatedKeran_k3_gradual_seroreversion,
  simulatedBassar_k3_gradual_seroreversion,
  sampleNum=sample_num_ov16)

for (sens_spec_val in sens_spec_options) {
  k3_gradual_seroreversion_simulation_summary_age_group_combined_sens_spec_list[[paste(sens_spec_val, collapse="_")]] <- summarizeSimulationData(combinedSimulation_k3_finite_seroreversion %>% mutate(sens = sens_spec_val[1], spec=sens_spec_val[2]), sens_spec_val, groupBySex=FALSE)
}

if(use_k4) {
  k4_gradual_seroreversion_simulation_summary_combined_sens_spec_list <- list()
  
  simulatedBassar_k4_gradual_seroreversion <- togo_bassar_gradual_seroreversion_agg$allOutputs %>% filter(Ke == 0.4) %>% fix_age_groups()
  
  for (sens_spec_val in sens_spec_options) {
    k4_gradual_seroreversion_simulation_summary_combined_sens_spec_list[[paste("bassar", sens_spec_val, collapse="_")]] <- summarizeSimulationData(simulatedBassar_k4_gradual_seroreversion %>% mutate(sens = sens_spec_val[1], spec=sens_spec_val[2]), sens_spec_val, groupBySex=FALSE, summary=TRUE)
  }
  
  simulatedOti_k4_gradual_seroreversion <- togo_oti_gradual_seroreversion_agg$allOutputs %>% filter(Ke == 0.4) %>% fix_age_groups()
  if (use_oti_100) {
    togo_oti_seroreversion_agg_vc_100 <- readRDS(paste("data/oti", oti_folder_100, "togo_oti_finite_seroreversion_data", place_to_pick, ".RDS", sep=""))
    simulatedOti_k4_seroreversion_vc_100 <- togo_oti_seroreversion_agg_vc_100$allOutputs %>% filter(Ke == 0.3) %>% fix_age_groups()
    simulatedOti_k4_gradual_seroreversion[
      simulatedOti_k4_gradual_seroreversion$vctr.ctrl.eff == 0.90,
    ] = simulatedOti_k4_seroreversion_vc_100
    simulatedOti_k4_gradual_seroreversion[
      simulatedOti_k4_gradual_seroreversion$vctr.ctrl.eff == 1,
    "vctr.ctrl.eff"] = 0.90
  }
  
  for (sens_spec_val in sens_spec_options) {
    k4_gradual_seroreversion_simulation_summary_combined_sens_spec_list[[paste("oti", sens_spec_val, collapse="_")]] <- summarizeSimulationData(simulatedOti_k4_gradual_seroreversion %>% mutate(sens = sens_spec_val[1], spec=sens_spec_val[2]), sens_spec_val, groupBySex=FALSE, summary=TRUE)
  }
  
  simulatedKeran_k4_gradual_seroreversion <- togo_keran_gradual_seroreversion_agg$allOutputs %>% filter(Ke == 0.4) %>% fix_age_groups()
  
  for (sens_spec_val in sens_spec_options) {
    k4_gradual_seroreversion_simulation_summary_combined_sens_spec_list[[paste("keran", sens_spec_val, collapse="_")]] <- summarizeSimulationData(simulatedKeran_k4_gradual_seroreversion %>% mutate(sens = sens_spec_val[1], spec=sens_spec_val[2]), sens_spec_val, groupBySex=FALSE, summary=TRUE)
  }
  
  k4_gradual_seroreversion_simulation_summary_combined_sens_spec_list <- list()
  combinedSimulation_k4_seroreversion <- selectRunsFromAllPrefectures(
    simulatedOti_k4_gradual_seroreversion,
    simulatedKeran_k4_gradual_seroreversion,
    simulatedBassar_k4_gradual_seroreversion,
    sampleNum=sample_num_ov16)
  for (sens_spec_val in sens_spec_options) {
    k4_gradual_seroreversion_simulation_summary_combined_sens_spec_list[[paste(sens_spec_val, collapse="_")]] <- summarizeSimulationData(combinedSimulation_k4_seroreversion %>% mutate(sens = sens_spec_val[1], spec=sens_spec_val[2]), sens_spec_val, groupBySex=FALSE)
  }
}

if(use_oti_100) {
  rm(togo_oti_seroreversion_agg_vc_100)
}
rm(togo_bassar_gradual_seroreversion_agg)
rm(togo_oti_gradual_seroreversion_agg)
rm(togo_keran_gradual_seroreversion_agg)
```

### Adjusting Simulation Data with a Distribution
Sensitivity and Specificity data pulled from a search of papers (see SI of Ramani et al. 2025). Using the data, we create a distribution to pull sens/spec from for each run of the model, whereas above we use a range of static sens/spec for all 1500 runs of the model for a given parameter set.
```{r distributions_sens_spec}
num_sens_specs <- 1500
sens_spec_from_dist <- c()
if ("sens_spec_list_from_dist_togo.rds" %in% list.files(paste0("images/images_", run_version))) {
  sens_spec_from_dist <- readRDS(paste0("images/images_", run_version, "/sens_spec_list_from_dist_togo.rds"))
}
if (length(sens_spec_from_dist) != num_sens_specs) {
  sens_from_dist <- pull_from_beta(beta_params_sens, num_sens_specs)
  spec_from_dist <- pull_from_beta(beta_params_spec, num_sens_specs)
  sens_spec_from_dist <- Map(c, sens_from_dist, spec_from_dist)
  sens_spec_from_dist %>% saveRDS(paste0("images/images_", run_version, "/sens_spec_list_from_dist_togo.rds"))
}

if ("oti_k3_100_mount_summary_adjusted_with_dist.rds" %in% list.files(paste0("images/images_", run_version))) {
  oti_k3_100_mount_simulation_summary_combined_dist_sens_spec <- readRDS(paste0("images/images_", run_version, "/oti_k3_100_mount_summary_adjusted_with_dist.rds"))
} else {
  oti_k3_100_mount_simulation_summary_combined_dist_sens_spec <- summarizeSimulationData(simulatedOti_k3_100_mount, sens_spec_from_dist, groupBySex=FALSE, summary=TRUE)
  oti_k3_100_mount_simulation_summary_combined_dist_sens_spec %>% saveRDS(paste0("images/images_", run_version, "/oti_k3_100_mount_summary_adjusted_with_dist.rds"))
}
k3_100_mount_simulation_summary_combined_sens_spec_list[[
  paste0(
    "oti", " ",
    round(oti_k3_100_mount_simulation_summary_combined_dist_sens_spec$all_ages$sens_mean[1], 2), "_",
    "oti", " ",
    round(oti_k3_100_mount_simulation_summary_combined_dist_sens_spec$all_ages$spec_mean[1], 2)
  )
]] <- oti_k3_100_mount_simulation_summary_combined_dist_sens_spec


if ("keran_k3_100_mount_summary_adjusted_with_dist.rds" %in% list.files(paste0("images/images_", run_version))) {
  keran_k3_100_mount_simulation_summary_combined_dist_sens_spec <- readRDS(paste0("images/images_", run_version, "/keran_k3_100_mount_summary_adjusted_with_dist.rds"))
} else {
  keran_k3_100_mount_simulation_summary_combined_dist_sens_spec <- summarizeSimulationData(simulatedKeran_k3_100_mount, sens_spec_from_dist, groupBySex=FALSE, summary=TRUE)
  keran_k3_100_mount_simulation_summary_combined_dist_sens_spec %>% saveRDS(paste0("images/images_", run_version, "/keran_k3_100_mount_summary_adjusted_with_dist.rds"))
}
k3_100_mount_simulation_summary_combined_sens_spec_list[[
  paste0(
    "keran", " ",
    round(keran_k3_100_mount_simulation_summary_combined_dist_sens_spec$all_ages$sens_mean[1], 2), "_",
    "keran", " ",
    round(keran_k3_100_mount_simulation_summary_combined_dist_sens_spec$all_ages$spec_mean[1], 2)
  )
]] <- keran_k3_100_mount_simulation_summary_combined_dist_sens_spec


if ("bassar_k3_100_mount_summary_adjusted_with_dist.rds" %in% list.files(paste0("images/images_", run_version))) {
  bassar_k3_100_mount_simulation_summary_combined_dist_sens_spec <- readRDS(paste0("images/images_", run_version, "/bassar_k3_100_mount_summary_adjusted_with_dist.rds"))
} else {
  bassar_k3_100_mount_simulation_summary_combined_dist_sens_spec <- summarizeSimulationData(simulatedBassar_k3_100_mount, sens_spec_from_dist, groupBySex=FALSE, summary=TRUE)
  bassar_k3_100_mount_simulation_summary_combined_dist_sens_spec %>% saveRDS(paste0("images/images_", run_version, "/bassar_k3_100_mount_summary_adjusted_with_dist.rds"))
}
k3_100_mount_simulation_summary_combined_sens_spec_list[[
  paste0(
    "bassar", " ",
    round(bassar_k3_100_mount_simulation_summary_combined_dist_sens_spec$all_ages$sens_mean[1], 2), "_",
    "bassar", " ",
    round(bassar_k3_100_mount_simulation_summary_combined_dist_sens_spec$all_ages$spec_mean[1], 2)
  )
]] <- bassar_k3_100_mount_simulation_summary_combined_dist_sens_spec


if ("comb_k3_100_mount_summary_adjusted_with_dist.rds" %in% list.files(paste0("images/images_", run_version))) {
  comb_k3_100_mount_simulation_summary_combined_dist_sens_spec <- readRDS(paste0("images/images_", run_version, "/comb_k3_100_mount_summary_adjusted_with_dist.rds"))
} else {
  comb_k3_100_mount_simulation_summary_combined_dist_sens_spec <- summarizeSimulationData(combinedSimulation_k3_100_mount, sens_spec_from_dist, groupBySex=FALSE)
  comb_k3_100_mount_simulation_summary_combined_dist_sens_spec %>% saveRDS(paste0("images/images_", run_version, "/comb_k3_100_mount_summary_adjusted_with_dist.rds"))
}
k3_100_mount_simulation_summary_age_group_combined_sens_spec_list[[
  paste0(
    round(comb_k3_100_mount_simulation_summary_combined_dist_sens_spec$sens_mean[1], 2), "_",
    round(comb_k3_100_mount_simulation_summary_combined_dist_sens_spec$spec_mean[1], 2)
  )
]] <- comb_k3_100_mount_simulation_summary_combined_dist_sens_spec

if ("oti_k3_instant_sero_summary_adjusted_with_dist.rds" %in% list.files(paste0("images/images_", run_version))) {
  oti_k3_instant_seroreversion_simulation_summary_combined_dist_sens_spec <- readRDS(paste0("images/images_", run_version, "/oti_k3_instant_sero_summary_adjusted_with_dist.rds"))
} else {
  oti_k3_instant_seroreversion_simulation_summary_combined_dist_sens_spec <- summarizeSimulationData(simulatedOti_k3_instant_seroreversion, sens_spec_from_dist, groupBySex=FALSE, summary=TRUE)
  oti_k3_instant_seroreversion_simulation_summary_combined_dist_sens_spec %>% saveRDS(paste0("images/images_", run_version, "/oti_k3_instant_sero_summary_adjusted_with_dist.rds"))
}
k3_instant_seroreversion_simulation_summary_combined_sens_spec_list[[
  paste0(
    "oti", " ",
    round(oti_k3_instant_seroreversion_simulation_summary_combined_dist_sens_spec$all_ages$sens_mean[1], 2), "_",
    "oti", " ",
    round(oti_k3_instant_seroreversion_simulation_summary_combined_dist_sens_spec$all_ages$spec_mean[1], 2)
  )
]] <- oti_k3_instant_seroreversion_simulation_summary_combined_dist_sens_spec

if ("keran_k3_instant_sero_summary_adjusted_with_dist.rds" %in% list.files(paste0("images/images_", run_version))) {
  keran_k3_instant_seroreversion_simulation_summary_combined_dist_sens_spec <- readRDS(paste0("images/images_", run_version, "/keran_k3_instant_sero_summary_adjusted_with_dist.rds"))
} else {
  keran_k3_instant_seroreversion_simulation_summary_combined_dist_sens_spec <- summarizeSimulationData(simulatedKeran_k3_instant_seroreversion, sens_spec_from_dist, groupBySex=FALSE, summary=TRUE)
  keran_k3_instant_seroreversion_simulation_summary_combined_dist_sens_spec %>% saveRDS(paste0("images/images_", run_version, "/keran_k3_instant_sero_summary_adjusted_with_dist.rds"))
}
k3_instant_seroreversion_simulation_summary_combined_sens_spec_list[[
  paste0(
    "keran", " ",
    round(keran_k3_instant_seroreversion_simulation_summary_combined_dist_sens_spec$all_ages$sens_mean[1], 2), "_",
    "keran", " ",
    round(keran_k3_instant_seroreversion_simulation_summary_combined_dist_sens_spec$all_ages$spec_mean[1], 2)
  )
]] <- keran_k3_instant_seroreversion_simulation_summary_combined_dist_sens_spec

if ("bassar_k3_instant_sero_summary_adjusted_with_dist.rds" %in% list.files(paste0("images/images_", run_version))) {
  bassar_k3_instant_seroreversion_simulation_summary_combined_dist_sens_spec <- readRDS(paste0("images/images_", run_version, "/bassar_k3_instant_sero_summary_adjusted_with_dist.rds"))
} else {
  bassar_k3_instant_seroreversion_simulation_summary_combined_dist_sens_spec <- summarizeSimulationData(simulatedBassar_k3_instant_seroreversion, sens_spec_from_dist, groupBySex=FALSE, summary=TRUE)
  bassar_k3_instant_seroreversion_simulation_summary_combined_dist_sens_spec %>% saveRDS(paste0("images/images_", run_version, "/bassar_k3_instant_sero_summary_adjusted_with_dist.rds"))
}
k3_instant_seroreversion_simulation_summary_combined_sens_spec_list[[
  paste0(
    "bassar", " ",
    round(bassar_k3_instant_seroreversion_simulation_summary_combined_dist_sens_spec$all_ages$sens_mean[1], 2), "_",
    "bassar", " ",
    round(bassar_k3_instant_seroreversion_simulation_summary_combined_dist_sens_spec$all_ages$spec_mean[1], 2)
  )
]] <- bassar_k3_instant_seroreversion_simulation_summary_combined_dist_sens_spec

if ("comb_k3_instant_sero_summary_adjusted_with_dist.rds" %in% list.files(paste0("images/images_", run_version))) {
  comb_k3_instant_seroreversion_simulation_summary_combined_dist_sens_spec <- readRDS(paste0("images/images_", run_version, "/comb_k3_instant_sero_summary_adjusted_with_dist.rds"))
} else {
  comb_k3_instant_seroreversion_simulation_summary_combined_dist_sens_spec <- summarizeSimulationData(combinedSimulation_k3_finite_seroreversion, sens_spec_from_dist, groupBySex=FALSE)
  comb_k3_instant_seroreversion_simulation_summary_combined_dist_sens_spec %>% saveRDS(paste0("images/images_", run_version, "/comb_k3_instant_sero_summary_adjusted_with_dist.rds"))
}
k3_instant_seroreversion_simulation_summary_age_group_combined_sens_spec_list[[
  paste0(
    round(comb_k3_instant_seroreversion_simulation_summary_combined_dist_sens_spec$sens_mean[1], 2), "_",
    round(comb_k3_instant_seroreversion_simulation_summary_combined_dist_sens_spec$spec_mean[1], 2)
  )
]] <- comb_k3_instant_seroreversion_simulation_summary_combined_dist_sens_spec

if ("oti_k3_gradual_sero_summary_adjusted_with_dist.rds" %in% list.files(paste0("images/images_", run_version))) {
  oti_k3_gradual_seroreversion_simulation_summary_combined_dist_sens_spec <- readRDS(paste0("images/images_", run_version, "/oti_k3_gradual_sero_summary_adjusted_with_dist.rds"))
} else {
  oti_k3_gradual_seroreversion_simulation_summary_combined_dist_sens_spec <- summarizeSimulationData(simulatedOti_k3_gradual_seroreversion, sens_spec_from_dist, groupBySex=FALSE, summary=TRUE)
  oti_k3_gradual_seroreversion_simulation_summary_combined_dist_sens_spec %>% saveRDS(paste0("images/images_", run_version, "/oti_k3_gradual_sero_summary_adjusted_with_dist.rds"))
}
k3_gradual_seroreversion_simulation_summary_combined_sens_spec_list[[
  paste0(
    "oti", " ",
    round(oti_k3_gradual_seroreversion_simulation_summary_combined_dist_sens_spec$all_ages$sens_mean[1], 2), "_",
    "oti", " ",
    round(oti_k3_gradual_seroreversion_simulation_summary_combined_dist_sens_spec$all_ages$spec_mean[1], 2)
  )
]] <- oti_k3_gradual_seroreversion_simulation_summary_combined_dist_sens_spec

if ("keran_k3_gradual_sero_summary_adjusted_with_dist.rds" %in% list.files(paste0("images/images_", run_version))) {
  keran_k3_gradual_seroreversion_simulation_summary_combined_dist_sens_spec <- readRDS(paste0("images/images_", run_version, "/keran_k3_gradual_sero_summary_adjusted_with_dist.rds"))
} else {
  keran_k3_gradual_seroreversion_simulation_summary_combined_dist_sens_spec <- summarizeSimulationData(simulatedKeran_k3_gradual_seroreversion, sens_spec_from_dist, groupBySex=FALSE, summary=TRUE)
  keran_k3_gradual_seroreversion_simulation_summary_combined_dist_sens_spec %>% saveRDS(paste0("images/images_", run_version, "/keran_k3_gradual_sero_summary_adjusted_with_dist.rds"))
}
k3_gradual_seroreversion_simulation_summary_combined_sens_spec_list[[
  paste0(
    "keran", " ",
    round(keran_k3_gradual_seroreversion_simulation_summary_combined_dist_sens_spec$all_ages$sens_mean[1], 2), "_",
    "keran", " ",
    round(keran_k3_gradual_seroreversion_simulation_summary_combined_dist_sens_spec$all_ages$spec_mean[1], 2)
  )
]] <- keran_k3_gradual_seroreversion_simulation_summary_combined_dist_sens_spec

if ("bassar_k3_gradual_sero_summary_adjusted_with_dist.rds" %in% list.files(paste0("images/images_", run_version))) {
  bassar_k3_gradual_seroreversion_simulation_summary_combined_dist_sens_spec <- readRDS(paste0("images/images_", run_version, "/bassar_k3_gradual_sero_summary_adjusted_with_dist.rds"))
} else {
  bassar_k3_gradual_seroreversion_simulation_summary_combined_dist_sens_spec <- summarizeSimulationData(simulatedBassar_k3_gradual_seroreversion, sens_spec_from_dist, groupBySex=FALSE, summary=TRUE)
  bassar_k3_gradual_seroreversion_simulation_summary_combined_dist_sens_spec %>% saveRDS(paste0("images/images_", run_version, "/bassar_k3_gradual_sero_summary_adjusted_with_dist.rds"))
}
k3_gradual_seroreversion_simulation_summary_combined_sens_spec_list[[
  paste0(
    "bassar", " ",
    round(bassar_k3_gradual_seroreversion_simulation_summary_combined_dist_sens_spec$all_ages$sens_mean[1], 2), "_",
    "bassar", " ",
    round(bassar_k3_gradual_seroreversion_simulation_summary_combined_dist_sens_spec$all_ages$spec_mean[1], 2)
  )
]] <- bassar_k3_gradual_seroreversion_simulation_summary_combined_dist_sens_spec

if ("comb_k3_gradual_sero_summary_adjusted_with_dist.rds" %in% list.files(paste0("images/images_", run_version))) {
  comb_k3_gradual_seroreversion_simulation_summary_combined_dist_sens_spec <- readRDS(paste0("images/images_", run_version, "/comb_k3_gradual_sero_summary_adjusted_with_dist.rds"))
} else {
  comb_k3_gradual_seroreversion_simulation_summary_combined_dist_sens_spec <- summarizeSimulationData(combinedSimulation_k3_finite_seroreversion, sens_spec_from_dist, groupBySex=FALSE)
  comb_k3_gradual_seroreversion_simulation_summary_combined_dist_sens_spec %>% saveRDS(paste0("images/images_", run_version, "/comb_k3_gradual_sero_summary_adjusted_with_dist.rds"))
}
k3_gradual_seroreversion_simulation_summary_age_group_combined_sens_spec_list[[
  paste0(
    round(comb_k3_gradual_seroreversion_simulation_summary_combined_dist_sens_spec$sens_mean[1], 2), "_",
    round(comb_k3_gradual_seroreversion_simulation_summary_combined_dist_sens_spec$spec_mean[1], 2)
  )
]] <- comb_k3_gradual_seroreversion_simulation_summary_combined_dist_sens_spec
```


## Plots

### MFP Plot Agg
```{r}
k3_mfp_df <- list()
for(pick in all_places_to_pick) {
  combinedSimulation_k3 <- selectRunsFromAllPrefectures(
    readRDS(paste("data/oti", folder, "togo_oti_100_mount_data", pick, ".RDS", sep=""))$allOutputs %>% filter(Ke == 0.3) %>% mutate(age_groups_old = case_when(
                                                age < 1 ~ 0,
                                                age < 5 ~ 2.5,
                                                age < 11 ~ 7.5,
                                                age < 16 ~ 13,
                                                age < 21 ~ 18,
                                                age < 26 ~ 23,
                                                age < 31 ~ 28,
                                                age < 36 ~ 33,
                                                age < 41 ~ 38,
                                                age < 46 ~ 43,
                                                age < 51 ~ 48,
                                                age < 56 ~ 53,
                                                age < 61 ~ 58,
                                                TRUE ~ 70.5
                                              )),
    readRDS(paste("data/keran", folder, "togo_keran_100_mount_data", pick, ".RDS", sep=""))$allOutputs %>% filter(Ke == 0.3) %>% mutate(age_groups_old = case_when(
                                                age < 1 ~ 0,
                                                age < 5 ~ 2.5,
                                                age < 11 ~ 7.5,
                                                age < 16 ~ 13,
                                                age < 21 ~ 18,
                                                age < 26 ~ 23,
                                                age < 31 ~ 28,
                                                age < 36 ~ 33,
                                                age < 41 ~ 38,
                                                age < 46 ~ 43,
                                                age < 51 ~ 48,
                                                age < 56 ~ 53,
                                                age < 61 ~ 58,
                                                TRUE ~ 70.5
                                              )),
    readRDS(paste("data/bassar", folder, "togo_bassar_100_mount_data", pick, ".RDS", sep=""))$allOutputs %>% filter(Ke == 0.3) %>% mutate(age_groups_old = case_when(
                                                age < 1 ~ 0,
                                                age < 5 ~ 2.5,
                                                age < 11 ~ 7.5,
                                                age < 16 ~ 13,
                                                age < 21 ~ 18,
                                                age < 26 ~ 23,
                                                age < 31 ~ 28,
                                                age < 36 ~ 33,
                                                age < 41 ~ 38,
                                                age < 46 ~ 43,
                                                age < 51 ~ 48,
                                                age < 56 ~ 53,
                                                age < 61 ~ 58,
                                                TRUE ~ 70.5
                                              )),
    sampleNum=c(500*0.22,500*0.37,500*0.41))
  
  if(length(k3_mfp_df) == 0) {
    k3_mfp_df <- summarizeSimulationData(combinedSimulation_k3 %>% mutate(sens = 1, spec=1), c(1,1), groupBySex=FALSE) %>% mutate(sample_time=pick)
  } else {
    k3_mfp_df <- rbind(k3_mfp_df,
                       summarizeSimulationData(combinedSimulation_k3 %>% mutate(sens = 1, spec=1), c(1,1), groupBySex=FALSE) %>% mutate(sample_time=pick))
  }
  gc()
}

mfp_plot <- ggplot() + geom_point(data=togoMFData, aes(x=age_groups, y=mf_prev*100, color="Observed Data")) +
  geom_errorbar(data=togoMFData, aes(x=age_groups, ymin=mf_wilson_lb*100, ymax=mf_wilson_ub*100), width=2.5, alpha=0.5) + 
  geom_line(data=k3_mfp_df %>% filter(sample_time == "_end_2015"), aes(x=age_groups, y=mf_prev*100, color=factor(vctr.ctrl.eff), linetype=sample_time), linewidth=1) +
  geom_ribbon(data=k3_mfp_df %>% filter(sample_time == "_end_2015"), aes(x=age_groups, ymin=mf_q1*100, ymax=mf_q3*100, color=factor(vctr.ctrl.eff), fill=factor(vctr.ctrl.eff), linetype=sample_time), alpha=0.1) +
  #geom_line(data=k4_mfp_df, aes(x=age_groups, y=mf_prev*100, color="Simulation K4")) +
  #geom_ribbon(data=k4_mfp_df, aes(x=age_groups, ymin=mf_lb*100, ymax=mf_ub*100), color="lightblue", fill="lightblue", linetype="dashed", alpha=0.2) +
  scale_color_manual("Type", values=c("black", "red", "lightblue", "green")) +
  scale_fill_manual("Type", values=c("black", "red", "lightblue", "green")) +
  scale_x_continuous(breaks=seq(0, 80, 5)) +
  xlab("Age (years)") +
  ylab("Microfilarial Prevalence (%)")
mfp_plot
ggsave(paste0("images/images_", run_version, "/togo_combined_mfp_graph.png"),mfp_plot, width=4250, height=3000, units="px", dpi=450)
```

### Clinical Infectious Disease Age-Group plots

#### LSR Values Prefectures
```{r}
use_calc_lsr_pref = TRUE
custom_calc_resid_pref_sampled_sens_spec <- function(data, sampled_sens_spec_from_dist, original_data, desc) {
  data$probs <- runif(dim(data)[1])
  results <- vector("list", length(sampled_sens_spec_from_dist))
  setDT(data)
  setDT(original_data)
  for (index in seq_along(sampled_sens_spec_from_dist)) {
    t0 <- proc.time()[3]
    sens_val <- sampled_sens_spec_from_dist[[index]][1]
    spec_val <- sampled_sens_spec_from_dist[[index]][2]
    
    tmp <- data[
      age_groups_lsr > 0, 
      .(
        sens = sens_val,
        spec = spec_val,
        H4 = calcSensSpecSeroPrev(ov16_pos_mating_any_mf, sens_val, spec_val, probs)
      ),
      by = .(run_num, prefecture, vctr.ctrl.eff)
    ]
    tmp_means <- tmp[, .(
        H4 = mean(H4)
      ), by = .(run_num, prefecture, vctr.ctrl.eff, sens, spec)
    ]
    tmp_means[original_data, on = "prefecture", `:=`(
      all_ages_lb = i.all_ages_lb,
      all_ages_ub = i.all_ages_ub,
      ov16_prev_all_ages = i.ov16_prev_all_ages
    )]
    tmp_means[, `:=`(
      in_ci = (H4 * 100 > all_ages_lb) & (H4 * 100 < all_ages_ub),
      mse_value = ((H4 * 100) - (ov16_prev_all_ages * 100))^2
    )]

    tmp_summary <- tmp_means[, .(
        in_ci = mean(in_ci),
        mse_value = mean(mse_value)
    ), by = .(prefecture, vctr.ctrl.eff, sens, spec)]
  
    results[[index]] <- tmp_summary[, .(
        mse_value,
        in_ci,
        vctr.ctrl.eff, 
        sens, 
        spec,
        prefecture,
        Hypothesis = "H4",
        run_num = index,
        Descriptor = desc
    )]
    t1 <- proc.time()[3]
    cat(
      sprintf(
        "Iteration %d (%f, %f) took %.3f seconds.\n", index, sens_val, spec_val, t1 - t0
      )
    )
  }
  all_results <- rbindlist(results)
  return(as.data.frame(all_results))
}
data_manip_resid_pref <- function(data, sens_spec, prefecture_name) {
  data$probs <- runif(dim(data)[1])
  data$sens <- sens_spec[1]
  data$spec <- sens_spec[2]
  if (sens_spec[1] < 0 | sens_spec[2] < 0) {
    data <- data %>% 
      group_by(run_num) %>%
      mutate(
        sens = first(pull_from_beta(beta_params_sens)),
        spec = first(pull_from_beta(beta_params_spec))
      )
  }
  return(
    data %>%
      filter(age_groups_lsr > 0) %>%
      group_by(run_num, vctr.ctrl.eff) %>% mutate(
      H4=calcSensSpecSeroPrev(ov16_pos_mating_any_mf, sens, spec, probs)
    ) %>% pivot_longer(
      cols=c(H4), names_to="Hypothesis", values_to = "ov16_prev"
    ) %>%
    group_by(run_num, vctr.ctrl.eff, Hypothesis, sens, spec) %>%
    summarise(
      ov16_prev = mean(ov16_prev),
      .groups="drop"
    ) %>%
    mutate(prefecture=prefecture_name)
  ) 
}
custom_calc_resid_pref <- function(original_data, new_data, desc) {
  merged_data <- merge(original_data, new_data, by=c("prefecture"))
  lsr_calculation <- merged_data %>%
    group_by(prefecture, Hypothesis, vctr.ctrl.eff, run_num) %>%
    mutate(
      in_ci = (
        (ov16_prev*100 > all_ages_lb) & 
        (ov16_prev*100 < all_ages_ub)
        ),
      mse_value = (
      ((ov16_prev*100) - (ov16_prev_all_ages*100))**2
      )
    ) %>%
    select(prefecture, Hypothesis, vctr.ctrl.eff, run_num, mse_value) %>%
    mutate(Descriptor = desc)
  return(lsr_calculation)
}

process_resids_pref <- function(resids, display_cis, combine_prefectures=list("oti/kpendjal"=-1, "keran"=-1, "bassar"=-1), normalize=FALSE, return_raw=FALSE) {
  final_columns <- c("spec", "sens", "Hypothesis", "oti/kpendjal_No Seroreversion", "oti/kpendjal_Instant Seroreversion", "oti/kpendjal_Finite Seroreversion", "keran_No Seroreversion", "keran_Instant Seroreversion","keran_Finite Seroreversion", "bassar_No Seroreversion", "bassar_Instant Seroreversion","bassar_Finite Seroreversion")
  oti_vc_eff_combined <- 0.75
  if (use_oti_100) {
    final_columns <- c(
      final_columns,
       "oti/kpendjal_vc_100_No Seroreversion", "oti/kpendjal_vc_100_Instant Seroreversion", "oti/kpendjal_vc_100_Finite Seroreversion"
    )
    oti_vc_eff_combined <- 1
  }
  final_resids <- resids %>%
    group_by(prefecture, vctr.ctrl.eff, sens_spec, Descriptor, Hypothesis) %>%
    # filter(Descriptor != "Instant Seroreversion") %>%
    summarise(
      sample_mean = mean(mse_value),
      sample_varience = var(mse_value),
      se = sqrt(sample_varience / n_distinct(run_num)),
      lower_bound = sample_mean - 1.96 * se,
      upper_bound = sample_mean + 1.96 * se,
      .groups="drop"
    ) %>%
    mutate(
      output_val = paste0(round(sample_mean, 2)),
      Hypothesis = factor(Hypothesis, levels=c("H1", "H2", "H3", "H4"))
    ) %>%
    separate(sens_spec, into = c("sens", "spec"), sep = ",", convert = TRUE)
  if (all(combine_prefectures > 0)) {
    final_resids <- final_resids %>%
      mutate(
        Descriptor = factor(Descriptor, levels=c("No Seroreversion", "Instant Seroreversion", "Finite Seroreversion")),
        prefecture = factor(prefecture, levels=c("oti/kpendjal", 'keran', 'bassar'))
      ) %>% 
      dplyr::select(prefecture, Descriptor, Hypothesis, vctr.ctrl.eff, spec, sens, sample_mean, lower_bound, upper_bound) %>%
      filter(
            (prefecture == "oti/kpendjal" & vctr.ctrl.eff==oti_vc_eff_combined) |
            (prefecture == "keran" & vctr.ctrl.eff==0.90) |
            (prefecture == "bassar" & vctr.ctrl.eff==0.60)
      ) %>%
      mutate(
        sample_mean = sample_mean * sapply(prefecture, function(x) combine_prefectures[[x]]),
        lower_bound = lower_bound * sapply(prefecture, function(x) combine_prefectures[[x]]),
        upper_bound = upper_bound * sapply(prefecture, function(x) combine_prefectures[[x]]),
      ) %>% 
      group_by(Descriptor, Hypothesis, sens, spec) %>%
      summarise(
        sample_mean = sum(sample_mean),
        lower_bound = sum(lower_bound),
        upper_bound = sum(upper_bound),
        .groups="drop"
      ) %>%
      mutate(output_val = paste0(round(sample_mean, 2)))
    if (return_raw) {
      return(
        final_resids %>%
          dplyr::select(Descriptor, sens, spec, Hypothesis, sample_mean, lower_bound, upper_bound)
      )
    }
    if (normalize) {
      final_resids <- final_resids %>%
        mutate(
          sample_mean = (sample_mean - min(sample_mean)) / (max(sample_mean) - min(sample_mean)),
          lower_bound = (lower_bound - min(lower_bound)) / (max(lower_bound) - min(lower_bound)),
          upper_bound = (upper_bound - min(upper_bound)) / (max(upper_bound) - min(upper_bound))
        ) %>%
        mutate(output_val = paste0(round(sample_mean, 2)))
    }
    if (display_cis) {
      final_resids <- final_resids %>%
        mutate(
          output_val = paste0(round(sample_mean, 2), " (", round(lower_bound, 2)," - ", round(upper_bound, 2),")")
        )
    }
    return (
      final_resids %>%
        pivot_wider(id_cols=c(spec, sens, Hypothesis), names_from=c(Descriptor), values_from=c(output_val)) %>%
        arrange(desc(spec), sens, Hypothesis)
    )
  }
  if(display_cis) {
    final_resids <- final_resids %>% 
      mutate(
        output_val = paste0(round(sample_mean, 2), " (", round(lower_bound, 2)," - ", round(upper_bound, 2),")")
      )
  }
  final_resids_df <- final_resids %>% 
    mutate(
      Descriptor = factor(Descriptor, levels=c("No Seroreversion", "Instant Seroreversion", "Finite Seroreversion")),
      prefecture = ifelse(prefecture == "oti/kpendjal" & vctr.ctrl.eff == 1, "oti/kpendjal_vc_100", prefecture),
      prefecture = factor(prefecture, levels=c("oti/kpendjal", 'keran', 'bassar', 'oti/kpendjal_vc_100'))
    ) %>%
    dplyr::select(prefecture, Descriptor, Hypothesis, vctr.ctrl.eff, spec, sens, sample_mean, lower_bound, upper_bound, output_val) %>%
    filter(
          (prefecture == "oti/kpendjal" & vctr.ctrl.eff==0.75) |
          (prefecture == "keran" & vctr.ctrl.eff==0.90) |
          (prefecture == "bassar" & vctr.ctrl.eff==0.60) |
          (prefecture == "oti/kpendjal_vc_100" & vctr.ctrl.eff==1)
    )
  if (return_raw) {
    return(
      final_resids_df %>%
        dplyr::select(Descriptor, prefecture, sens, spec, Hypothesis, sample_mean, lower_bound, upper_bound)
    )
  }
  final_resids_df <- final_resids_df %>%
    select(
      -sample_mean, -lower_bound, -upper_bound
    ) %>%
    pivot_wider(id_cols=c(spec, sens, Hypothesis), names_from=c(prefecture, Descriptor), values_from=c(output_val)) %>% group_by(Hypothesis) %>% 
    ungroup() %>% 
    select(all_of(final_columns)) %>%
    arrange(desc(spec), sens, Hypothesis)
  
  return(
     final_resids_df
  )
}

if (use_calc_lsr_pref) {
  resids_pref = c()
  for(sens_spec in sens_spec_options_2) {
    print(sens_spec)
    if (all(sens_spec == c(-1, -1))) {
      new_result <- rbind(
        custom_calc_resid_pref_sampled_sens_spec(
          rbind(
            simulatedOti_k3_100_mount %>% mutate(prefecture ="oti/kpendjal"),
            simulatedKeran_k3_100_mount %>% mutate(prefecture ="keran"),
            simulatedBassar_k3_100_mount %>% mutate(prefecture ="bassar")
          ),
          sens_spec_from_dist,
          groupedVillageData %>% mutate(prefecture=tolower(prefecture)),
          "No Seroreversion"
        ),
        custom_calc_resid_pref_sampled_sens_spec(
          rbind(
            simulatedOti_k3_instant_seroreversion %>% mutate(prefecture ="oti/kpendjal"),
            simulatedKeran_k3_instant_seroreversion %>% mutate(prefecture ="keran"),
            simulatedBassar_k3_instant_seroreversion %>% mutate(prefecture ="bassar")
          ),
          sens_spec_from_dist,
          groupedVillageData %>% mutate(prefecture=tolower(prefecture)),
          "Instant Seroreversion"
        ),
        custom_calc_resid_pref_sampled_sens_spec(
          rbind(
            simulatedOti_k3_gradual_seroreversion %>% mutate(prefecture ="oti/kpendjal"),
            simulatedKeran_k3_gradual_seroreversion %>% mutate(prefecture ="keran"),
            simulatedBassar_k3_gradual_seroreversion %>% mutate(prefecture ="bassar")
          ),
          sens_spec_from_dist,
          groupedVillageData %>% mutate(prefecture=tolower(prefecture)),
          "Finite Seroreversion"
        )
      )
    } else {
      new_result <- rbind(
          custom_calc_resid_pref(
            groupedVillageData %>% mutate(prefecture=tolower(prefecture)),
            rbind(
              data_manip_resid_pref(simulatedOti_k3_100_mount, sens_spec, "oti/kpendjal"),
              data_manip_resid_pref(simulatedKeran_k3_100_mount, sens_spec, "keran"),
              data_manip_resid_pref(simulatedBassar_k3_100_mount, sens_spec, "bassar")#,
              #data_manip_resid_pref(simulatedOti_k3_100_mount_vc_100, sens_spec, "oti/kpendjal")
            ),
            "No Seroreversion"),
          custom_calc_resid_pref(
            groupedVillageData %>% mutate(prefecture=tolower(prefecture)),
            rbind(
              data_manip_resid_pref(simulatedOti_k3_instant_seroreversion, sens_spec, "oti/kpendjal"),
              data_manip_resid_pref(simulatedKeran_k3_instant_seroreversion, sens_spec, "keran"),
              data_manip_resid_pref(simulatedBassar_k3_instant_seroreversion, sens_spec, "bassar")#,
              #data_manip_resid_pref(simulatedOti_k3_instant_seroreversion_vc_100, sens_spec, "oti/kpendjal")
            ),
            "Instant Seroreversion"),
          custom_calc_resid_pref(
            groupedVillageData %>% mutate(prefecture=tolower(prefecture)),
            rbind(
              data_manip_resid_pref(simulatedOti_k3_gradual_seroreversion, sens_spec, "oti/kpendjal"),
              data_manip_resid_pref(simulatedKeran_k3_gradual_seroreversion, sens_spec, "keran"),
              data_manip_resid_pref(simulatedBassar_k3_gradual_seroreversion, sens_spec, "bassar")#,
              #data_manip_resid_pref(simulatedOti_k3_gradual_seroreversion_vc_100, sens_spec, "oti/kpendjal")
            ),
            "Finite Seroreversion")
      )
    }
    new_result$sens_spec <- paste0(sens_spec, collapse=", ")
    if (length(resids_pref) == 0) {
      resids_pref <- new_result
    } else {
      resids_pref <- rbind(
        resids_pref,
        new_result
      )
    }
  }
  
  resids_pref %>% write.csv(paste0("images/images_", run_version, "/raw_resids_pref.csv"), row.names=FALSE)
  #process_resids_pref(resids_pref, FALSE)
  resids <- process_resids_pref(resids_pref, TRUE)
  resids %>% kable('html', escape=FALSE) %>% kable_classic() %>% print()
  resids %>% write.csv(paste0("images/images_", run_version, "/base_resids_togo.csv"), row.names=FALSE)
  resids <- process_resids_pref(resids_pref, TRUE, combine_prefectures = c(0.394, 0.552, 0.054))
  resids %>% kable('html', escape=FALSE) %>% kable_classic() %>% print()
  resids %>% write.csv(paste0("images/images_", run_version, "/combined_resids_togo.csv"), row.names=FALSE)
  resids <- process_resids_pref(resids_pref, TRUE, combine_prefectures = c(0.394, 0.552, 0.054), normalize=TRUE)
  resids %>% kable('html', escape=FALSE) %>% kable_classic() %>% print()
  resids %>% write.csv(paste0("images/images_", run_version, "/combined_and_normalized_resids_togo.csv"), row.names=FALSE)
}

raw_resids_df <- read.csv(paste0("images/images_", run_version, "/raw_resids_pref.csv")) 

combined_raw_resids <- process_resids_pref(raw_resids_df, TRUE, combine_prefectures = c(0.394, 0.552, 0.054), return_raw=TRUE) %>%
  mutate(
    serorev_hyp = case_when(
      grepl("Finite", Descriptor) ~ "(iii)",
      grepl("Instant", Descriptor) ~ "(ii)",
      TRUE ~ "(i)"
    )
  ) %>%
  filter(sens == -1 & serorev_hyp != "(i)") %>%
  mutate(
    min_val = min(sample_mean, lower_bound, upper_bound),
    max_val = max(sample_mean, lower_bound, upper_bound),
    normalized_mean_mse = (
      (sample_mean - min_val) / (max_val - min_val)
    ),
    normalized_lower_bound = (
      (lower_bound - min_val) / (max_val - min_val)
    ),
    normalized_upper_bound = (
      (upper_bound - min_val) / (max_val - min_val)
    ),
    label_val = paste0(
      signif(normalized_mean_mse, 2), "\n(",
      signif(normalized_lower_bound, 2), " - ",
      signif(normalized_upper_bound, 2), ")"
    )
  )

combined_heat_map <- ggplot(
  data = combined_raw_resids
) +
  geom_tile(
    aes(
      x=serorev_hyp,
      y=1,
      fill=normalized_mean_mse
    )
  ) +
  geom_text(
    aes(
      x=serorev_hyp,
      y=1,
      label=label_val,
      color=ifelse(normalized_mean_mse > 0.5, "black", "white")
    ),
    size=5
  ) +
  scale_color_identity() +
  # scale_fill_viridis_c("Normalized MSE", option = "rocket", breaks=seq(0, 1, 0.5)) + 
  scale_fill_gradientn(
    "Normalized MSE",
    colours = c("black", "grey20", "grey50", "grey70", "white"),# "#f58a1f"),
    breaks=seq(0, 1, 0.5),
    limits=c(0, 1)
  ) +
  theme_bw() +
  theme(
    panel.border = element_blank(),
    strip.background = element_blank(),
    axis.text = element_text(face="bold"),
    legend.direction = "horizontal",
    legend.position = "bottom",
    axis.line.y = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank()
  ) +
  guides(
    fill=guide_colorbar(title.position = "top", title.hjust=0.5)
  ) +
  xlab("") +
  ylab("")
combined_heat_map

prefecture_raw_resids <- process_resids_pref(raw_resids_df, TRUE, return_raw=TRUE) %>%
  mutate(
    prefecture = factor(
      case_when(
        grepl("oti", prefecture) ~ "Oti/Kpendjal",
        grepl("keran", prefecture) ~ "Keran",
        TRUE ~ "Bassar"
      ),
      levels = c("Oti/Kpendjal", "Keran", "Bassar")
    ),
    serorev_hyp = case_when(
      grepl("Finite", Descriptor) ~ "(iii)",
      grepl("Instant", Descriptor) ~ "(ii)",
      TRUE ~ "(i)"
    )
  ) %>%
  filter(sens == -1 & serorev_hyp != "(i)") %>%
  group_by(prefecture) %>%
  mutate(
    min_val = min(sample_mean, lower_bound, upper_bound),
    max_val = max(sample_mean, lower_bound, upper_bound),
    normalized_mean_mse = (
      (sample_mean - min_val) / (max_val - min_val)
    ),
    normalized_lower_bound = (
      (lower_bound - min_val) / (max_val - min_val)
    ),
    normalized_upper_bound = (
      (upper_bound - min_val) / (max_val - min_val)
    ),
    label_val = paste0(
      signif(normalized_mean_mse, 1), "\n(",
      signif(normalized_lower_bound, 1), " - ",
      signif(normalized_upper_bound, 1), ")"
    )
  )

prefecture_heat_map <- ggplot(
  data = prefecture_raw_resids
) +
  geom_tile(
    aes(
      x=prefecture,
      y=serorev_hyp,
      fill=normalized_mean_mse
    )
  ) +
  geom_text(
    aes(
      x=prefecture,
      y=serorev_hyp,
      label=label_val,
      color=ifelse(normalized_mean_mse > 0.5, "black", "white")
    ),
    size=5
  ) +
  scale_color_identity() +
  # scale_fill_viridis_c("Normalized MSE", option = "rocket", breaks=seq(0, 1, 0.5)) + 
  scale_fill_gradientn(
    "Normalized MSE",
    colours = c("black", "grey20", "grey50", "grey70", "white"),# "#f58a1f"),
    breaks=seq(0, 1, 0.5),
    limits=c(0, 1)
  ) +
  theme_bw() +
  theme(
    panel.border = element_blank(),
    strip.background = element_blank(),
    axis.text = element_text(face="bold"),
    legend.direction = "horizontal",
    legend.position = "bottom"
  ) +
  guides(
    fill=guide_colorbar(title.position = "top", title.hjust=0.5)
  ) +
  xlab("") +
  ylab("")
prefecture_heat_map


ggsave(
  paste0("images/images_", run_version, "/togo_combined_normalized_mse.svg"),
  combined_heat_map,
  width=4250, height=3000, units="px", dpi=600
)


```

#### Age Grouped Graphs

```{r cid_graph_function}
filterHypotheses <- function(data) {
  # actual_hyps <- c("Patent Infection")
  # data <- data %>% filter(Hypothesis %in% actual_hyps) %>% mutate(
  #   Hypothesis = "Mating worm pair with any mf"
  # )
  return(data)
}

makeAgeGroupGraphsSensSpec <- function(originalData, projection_df_list, descriptor, facet_value="sens ~ spec", facet_1, facet_2, ignore_sens_spec_val="") {
  originalData <- originalData %>% filter(age_groups != 0.0)
  combined_df <- NA
  for(sens_spec_val in names(projection_df_list)) {
    if (sens_spec_val == ignore_sens_spec_val) {
      next
    }
    if(!is.data.frame(combined_df)) {
      combined_df <- projection_df_list[[sens_spec_val]] %>% mutate(sens_spec = sens_spec_val)
    } else {
      combined_df <- rbind(combined_df, projection_df_list[[sens_spec_val]] %>% mutate(sens_spec = sens_spec_val))
    }
  }

  combined_df_2 <- combined_df %>% separate_wider_delim(sens_spec, delim="_", names=c("sens", "spec"))
  
  #vct_ctrl_list <- combined_df_2 %>% select(vctr.ctrl.eff) %>% distinct() %>% .[[1]]
  #for(vct_ctr in vct_ctrl_list) {
    tmp_projection_data <- combined_df_2 %>% 
      #filter(vctr.ctrl.eff == vct_ctr) %>% 
      mutate(vctr.ctrl.eff = paste(as.numeric(vctr.ctrl.eff)*100, "%", sep="")) %>% 
      mutate(
        sens = paste(as.numeric(sens)*100, "%", sep=""),
        spec = paste(as.numeric(spec)*100, "%", sep="")
      ) %>% filterHypotheses()
    

    

    color_vals <- c("Mating worm pair with any mf"="darkred", "Patent Infection"="darkred", "Pre-Patent Infection"="blue")
    color_vals <- c("60%"="brown", "75%"="red", "95%"="orange")
    #color_vals <- c("60%"="black", "75%" = "black", "95%" = "black")
    linetype_vals <- c("60%"="solid", "75%"="dashed", "95%"="dotted", "none"="none")
    p1 <- ggplot() + 
      geom_line(
        aes(x=age_groups, y=ov16_prev*100, 
            linetype=factor(vctr.ctrl.eff),
            color=vctr.ctrl.eff#Hypothesis
            ), 
        linewidth=0.5, data=tmp_projection_data
      ) +
      geom_ribbon(
        aes(x=age_groups, ymin=ov16_q1*100, ymax=ov16_q3*100,
            fill=vctr.ctrl.eff,
            linetype=vctr.ctrl.eff
            ),
        alpha=0.1,
        linewidth=0.1,
        data=tmp_projection_data
      ) +
      geom_point(
        aes(x=age_groups, y=ov16_seroprev*100), 
        color="black", alpha=0.5, data=originalData, size=0.5
      ) +
      geom_errorbar(
        aes(x=age_groups, ymin=ov16_wilson_lb*100, ymax=ov16_wilson_ub*100), 
        width=2.5, alpha=0.5, color="black", data=originalData
      ) +
      xlab("Age (years)") + ylab("Anti-Ov16 seroprevalence (%)") +
      #scale_color_manual("Hypotheses", values=color_vals) +
      scale_color_manual("Vector control efficacy", values=color_vals) +
      scale_fill_manual("Vector control efficacy", values=color_vals) +
      scale_linetype_manual("Vector control efficacy", values=linetype_vals) +
      #guides(
      #  linetype = guide_legend(order = 1), 
      #  color = guide_legend(order = 2)
      #) +
      theme_bw() +
      facet_grid(facet_value) +
      scale_y_continuous(
        limits=c(0, 101), 
        breaks=seq(0, 100, 25), 
        sec.axis = sec_axis(~ . , name = facet_1, breaks = NULL, labels = NULL)
      ) +
      scale_x_continuous(
        limits=c(0, 81), 
        breaks=seq(0, 100, 20) 
        #sec.axis = sec_axis(~ . , name = facet_2, breaks = NULL, labels = NULL)
      ) +
      ggtitle(facet_2) +
      theme_bw() +
      theme(
        plot.title = element_text(size=10, hjust = 0.5),
        axis.title.y = element_text(size=10),
        title = element_text(size=10),
        legend.text = element_text(size=6),
        legend.title = element_text(size=8),
        legend.key.size = unit(0.8, 'lines'),
        legend.position = "bottom",  # Set legend to the bottom
        legend.direction = "horizontal",
        axis.text.y = element_text(size=6),
        axis.text.x = element_text(size=6),
        strip.placement = "outside",
        panel.grid.minor = element_blank(),
        axis.line.x = element_line(color = "black"),
        axis.line.y = element_line(color = "black"),
        strip.text.y = element_text(angle=0),
        axis.line.y.right = element_blank()
      )
      #ggtitle(paste("Vector Control Efficacy:", vct_ctr*100))
    #ggsave(paste("images/togo_sens_spec_analysis_", descriptor, "_", vct_ctr, ".png", sep=""), p1, units="in", height=4, width=5.5, dpi=300)
    ggsave(paste("images/images_", run_version, "/togo_sens_spec_analysis_", descriptor, ".png", sep=""), p1, units="in", height=4, width=5.5, dpi=300)
    print(p1)
  #}
}

makeAgeGroupGraphsSensSpec(togoOv16Data, k3_100_mount_simulation_summary_age_group_combined_sens_spec_list, paste0("basic"), "sens ~ spec", "Sensitivity", "Specificity", ignore_sens_spec_val="0.76_0.83")

makeAgeGroupGraphsSensSpec(togoOv16Data, k3_instant_seroreversion_simulation_summary_age_group_combined_sens_spec_list, paste0("instant_seroreversion"), "sens ~ spec", "Sensitivity", "Specificity", ignore_sens_spec_val="0.76_0.83")

makeAgeGroupGraphsSensSpec(togoOv16Data, k3_gradual_seroreversion_simulation_summary_age_group_combined_sens_spec_list, paste0("gradual_seroreversion"), "sens ~ spec", "Sensitivity", "Specificity", ignore_sens_spec_val="0.76_0.83")

if (use_k4) {
  makeAgeGroupGraphsSensSpec(togoOv16Data, k4_100_mount_simulation_summary_age_group_combined_sens_spec_list, paste0("basic_k4_", run_version), "sens ~ spec", "Sensitivity", "Specificity")

  makeAgeGroupGraphsSensSpec(togoOv16Data, k4_instant_seroreversion_simulation_summary_age_group_combined_sens_spec_list, paste0("instant_seroreversion_k4"), "sens ~ spec", "Sensitivity", "Specificity")
  
  makeAgeGroupGraphsSensSpec(togoOv16Data, k3_gradual_seroreversion_simulation_summary_age_group_combined_sens_spec_list, paste0("gradual_seroreversion_k4"), "sens ~ spec", "Sensitivity", "Specificity")
}
```

#### Prefecture Bar Charts

```{r}
makePrefectureBarSensSpec <- function(original_data, projection_df_list, use_all_age=TRUE, descriptor="", sero_dfs=list()) {
  ylab <- "all ages"
  if (grepl("under10", descriptor)) {
    ylab <- "under 10 year-old"
  }
  color_vals <- c("Observed"="black", "Any worm"="blue", "L3 exposure"="purple", "L4-L5 moult"="#6366f2", "Mating worm pair"="brown", "Mating worm pair with any mf"="red", "Mating worm pair with detectable mf"="orange")
  color_vals <- c("Observed"="black", "VCE: 60%"="brown", "VCE: 75%"="red", "VCE: 95%"="orange", "VCE: 60%*"="blue", "VCE: 75%*"="purple", "VCE: 95%*"="#6366f2")
  fill_vals <- c("Observed"="black", "VCE: 60%"="brown", "VCE: 75%"="red", "VCE: 95%"="orange", "VCE: 60%*"="white", "VCE: 75%*"="white", "VCE: 95%*"="white")
  color_vals <- c("Observed"="black", "Observed Error Bar"= "red", "Error Bar"= "black", "VCE: 60%"="black", "VCE: 75%"="black", "VCE: 95%"="black", "VCE: 60%*"="brown", "VCE: 75%*"="red", "VCE: 95%*"="orange")
  error_bar_colors <- c("Observed"="red", "Any worm"="red", "L3 exposure"="red", "L4-L5 moult"="red", "Mating worm pair"="red", "Mating worm pair with any mf"="red", "Mating worm pair with detectable mf"="red")
  error_bar_colors <- c("Observed"="red", "VCE: 60%"="black", "VCE: 75%"="black", "VCE: 95%"="black", "VCE: 60%*"="black", "VCE: 75%*"="black", "VCE: 95%*"="black")
  combined_df <- NA
  for(sens_spec_val in names(projection_df_list)) {
    df_to_use <- projection_df_list[[sens_spec_val]]$all_ages
    if(length(sero_dfs) > 0) {
      df_to_use <- df_to_use %>% mutate(seroreversion = FALSE)
      df_to_use <- rbind(df_to_use, sero_dfs[[sens_spec_val]]$all_ages %>% mutate(seroreversion = TRUE))
    }
    if (!use_all_age) {
      df_to_use <- projection_df_list[[sens_spec_val]]$under10
      if(length(sero_dfs) > 0) {
        df_to_use <- df_to_use %>% mutate(seroreversion = FALSE)
        df_to_use <- rbind(df_to_use, sero_dfs[[sens_spec_val]]$under10 %>% mutate(seroreversion = TRUE))
      }
    }
    sens_spec_val_to_use = str_replace_all(sens_spec_val, "oti", "oti/kpendjal")
    if(!is.data.frame(combined_df)) {
      combined_df <- df_to_use %>% mutate(sens_spec = sens_spec_val_to_use)
    } else {
      combined_df <- rbind(combined_df, df_to_use %>% mutate(sens_spec = sens_spec_val_to_use))
    }
    
    filtered_original_df <- original_data %>% mutate(prefecture=tolower(prefecture)) %>% filter(str_detect(sens_spec_val_to_use, prefecture))
    if(use_all_age) {
      combined_df <- rbind(
        combined_df,
        list(
          # ov16 lb, ub, prev, mf q1, q3, prev, sero, sens spec
          c(-1, -1),
          rep("Observed", 2), 
          rep(filtered_original_df$all_ages_lb, 2) / 100,
          rep(filtered_original_df$all_ages_ub, 2) / 100,
          rep(filtered_original_df$ov16_prev_all_ages, 2),
          rep(NA, 2),
          rep(NA, 2),
          rep(NA, 2),
          c(FALSE, TRUE),
          rep(sens_spec_val_to_use, 2)
        )
      )
    } else {
      combined_df <- rbind(
        combined_df,
        list(
          # ov16 lb, ub, prev, mf q1, q3, prev, sero, sens spec
          c(-1, -1), 
          rep("Observed", 2), 
          rep(filtered_original_df$children_lb, 2) / 100,
          rep(filtered_original_df$children_ub, 2) / 100,
          rep(filtered_original_df$ov16_prev_children, 2),
          rep(NA, 2),
          rep(NA, 2),
          rep(NA, 2),
          c(FALSE, TRUE),
          rep(sens_spec_val_to_use, 2)
        )
      )
    }
  }
  combined_df_2 <- combined_df %>% 
    separate_wider_delim(sens_spec, delim="_", names=c("sens", "spec")) %>%
    separate_wider_delim(sens, delim=" ", names=c("prefecture", "sens")) %>%
    separate_wider_delim(spec, delim=" ", names=c("to_drop", "spec")) %>%
    select(-to_drop) %>% 
    filter(Hypothesis %in% c(
                            "Observed", 
                            #"L3 exposure", 
                            #"L4-L5 moult",
                            #"Any worm", 
                            "Mating worm pair with any mf"
                          )) %>%
    mutate(
      prefecture = factor(str_to_title(prefecture), levels=c("Oti/Kpendjal", "Keran", "Bassar")),
      Hypothesis = factor(Hypothesis,
                          c(
                            "Observed", 
                            "L3 exposure", 
                            "L4-L5 moult",
                            "Any worm", 
                            "Mating worm pair with any mf"
                          )),
      error_bar_colors = ifelse(vctr.ctrl.eff < 0, "Observed Error Bar", "Error Bar"),
      vctr.ctrl.eff = ifelse(vctr.ctrl.eff > 0, paste("VCE: ", as.numeric(vctr.ctrl.eff)*100, "%", sep=""), "Observed"),
      vctr.ctrl.eff = ifelse(seroreversion == TRUE & vctr.ctrl.eff != "Observed", paste0(vctr.ctrl.eff, "*"), vctr.ctrl.eff),
      vctr.ctrl.eff = factor(vctr.ctrl.eff, levels=c("Observed", "VCE: 60%", "VCE: 60%*", "VCE: 75%", "VCE: 75%*", "VCE: 95%", "VCE: 95%*")),
      seroreversion = ifelse(seroreversion, "S", "NS"),
      seroreversion = ifelse(vctr.ctrl.eff == "Observed", "", seroreversion),
      sens = paste(as.numeric(sens)*100, "%", sep=""),
      spec = paste(as.numeric(spec)*100, "%", sep="")
    )

  if(!use_all_age) {
    combined_df_2 <- combined_df_2 %>% filter(prefecture != "Bassar")
  }

  vct_ctrl_list <- combined_df_2 %>% select(vctr.ctrl.eff) %>% distinct() %>% .[[1]]
  #for(vctr.ctrl in vct_ctrl_list) {
    #plot <- ggplot(data=(combined_df_2 %>% filter(vctr.ctrl.eff == 0.6))) + 
    plot <- ggplot(data=combined_df_2) + # %>% filter(!grepl("\\*", vctr.ctrl.eff))) + 
      #geom_bar(aes(x=prefecture, y=ov16_prev*100, fill=Hypothesis), position="dodge", stat="identity") + 
      #geom_errorbar(aes(x=prefecture, ymin=ov16_prev_lb*100, ymax=ov16_prev_ub*100, group=Hypothesis, color=Hypothesis), alpha=0.5, position="dodge") +
      geom_bar(aes(x=prefecture, y=ov16_prev*100, fill=vctr.ctrl.eff, color=vctr.ctrl.eff), position=position_dodge(width=0.9), width=0.6, stat="identity") + 
      geom_errorbar(aes(x=prefecture, ymin=ov16_prev_lb*100, ymax=ov16_prev_ub*100, group=vctr.ctrl.eff, color=error_bar_colors), width=0.3, position=position_dodge(width=0.9)) +
      #geom_text(aes(x=prefecture, y=0, group=vctr.ctrl.eff, label=seroreversion), position = position_dodge(width=0.9), vjust = 1.5, size=1) +
      scale_fill_manual("", values=fill_vals,
                        breaks=c(
                           "Observed",
                           "VCE: 60%*",
                           "VCE: 60%",
                           "VCE: 75%*",
                           "VCE: 75%",
                           "VCE: 95%*",
                           "VCE: 95%"
                         ),
                         labels=c(
                           "Observed",
                           "Vector control efficacy: 60%*",
                           "Vector control efficacy: 60%",
                           "Vector control efficacy: 75%*",
                           "Vector control efficacy: 75%",
                           "Vector control efficacy: 95%*",
                           "Vector control efficacy: 95%"
                         )) +#color_vals) +
      scale_color_manual("", values=color_vals,
                         breaks=c(
                           "Observed",
                           "VCE: 60%*",
                           "VCE: 60%",
                           "VCE: 75%*",
                           "VCE: 75%",
                           "VCE: 95%*",
                           "VCE: 95%"
                         ),
                         labels=c(
                           "Observed",
                           "Vector control efficacy: 60%*",
                           "Vector control efficacy: 60%",
                           "Vector control efficacy: 75%*",
                           "Vector control efficacy: 75%",
                           "Vector control efficacy: 95%*",
                           "Vector control efficacy: 95%"
                         )) +#error_bar_colors) +
      #scale_alpha_manual("Seroreversion", values=c(1, 0.5)) +
      facet_grid(sens ~ spec) +
      xlab("Prefecture") +
      scale_y_continuous(
        paste("Anti-Ov16", ylab, "seroprevalence (%)"),
        limits = c(-5, max(combined_df_2$ov16_prev_ub*100)),
        breaks=seq(0, 60, 20),
        sec.axis = sec_axis(~ . , name = "Sensitivity", breaks = NULL, labels = NULL)
      ) +
      ggtitle("Specificity") +
      theme_bw() +
      theme(
          plot.title = element_text(size=10, hjust = 0.5),
          axis.title.y = element_text(size=10),
          title = element_text(size=10),
          legend.text = element_text(size=6),
          legend.title = element_text(size=8),
          legend.key.size = unit(0.8, 'lines'),
          legend.position = "bottom",  # Set legend to the bottom
          legend.direction = "horizontal",
          axis.text.y = element_text(size=6),
          axis.text.x = element_text(size=6, angle=70, vjust=0.5),
          strip.placement = "outside",
          panel.border = element_blank(),
          panel.grid.major.x = element_blank(),
          panel.grid.minor.x = element_blank(),
          axis.line.x = element_line(color = "black"),
          axis.line.y = element_line(color = "black"),
          strip.text.y = element_text(angle=0),
          axis.line.y.right = element_blank()
        ) +
      geom_segment(aes(x=0.55, xend=1.45, y=-5, yend=-5), color="black", size=0.1) +
      geom_segment(aes(x=0.55, xend=0.55, y=0, yend=-5), color="black", size=0.1) +
      geom_segment(aes(x=1.45, xend=1.45, y=0, yend=-5), color="black", size=0.1) + 
      geom_segment(aes(x=1.55, xend=2.45, y=-5, yend=-5), color="black", size=0.1) +
      geom_segment(aes(x=1.55, xend=1.55, y=0, yend=-5), color="black", size=0.1) +
      geom_segment(aes(x=2.45, xend=2.45, y=0, yend=-5), color="black", size=0.1)
    if(use_all_age) {
      plot <- plot + 
        geom_segment(aes(x=2.55, xend=3.45, y=-5, yend=-5), color="black", size=0.1) +
        geom_segment(aes(x=2.55, xend=2.55, y=0, yend=-5), color="black", size=0.1) +
        geom_segment(aes(x=3.45, xend=3.45, y=0, yend=-5), color="black", size=0.1)
    }
      #guides(color="none")
    print(plot)
    #ggsave(paste("images/togo_sens_spec_analysis_bar_", descriptor, "_", vctr.ctrl, ".png", sep=""), plot, units="in", height=4, width=5.5, dpi=300)
    ggsave(paste("images/images_", run_version, "/togo_sens_spec_analysis_bar_", descriptor, ".png", sep=""), plot, units="in", height=5, width=6, dpi=300)
  #}
}

makePrefectureBarSensSpec(groupedVillageData, k3_100_mount_simulation_summary_combined_sens_spec_list, TRUE, paste0("instant_all_ages"), k3_instant_seroreversion_simulation_summary_combined_sens_spec_list)

makePrefectureBarSensSpec(groupedVillageData, k3_100_mount_simulation_summary_combined_sens_spec_list, FALSE, paste0("instant_under10"), k3_instant_seroreversion_simulation_summary_combined_sens_spec_list)

makePrefectureBarSensSpec(groupedVillageData, k3_100_mount_simulation_summary_combined_sens_spec_list, TRUE, paste0("gradual_all_ages"), k3_gradual_seroreversion_simulation_summary_combined_sens_spec_list)

makePrefectureBarSensSpec(groupedVillageData, k3_100_mount_simulation_summary_combined_sens_spec_list, FALSE, paste0("gradual_under10"), k3_gradual_seroreversion_simulation_summary_combined_sens_spec_list)

```

### Using Best Fit Treatment Scenarios

#### Prefectures Using Just Best Fit VCs
```{r}
makePrefectureBarSensSpecBestFit <- function(original_data, projection_df_list, use_all_age=TRUE, descriptor="", sero_dfs=list(), use_dist_sens_spec=FALSE, sero_val=FALSE, hyps=c("H4i", "H4iii")) {
  ylab <- "all ages"
  if (grepl("under10", descriptor)) {
    ylab <- "under 10 year-old"
  }

  pattern_vals <- c("none", "none", "stripe")
  names(pattern_vals) <- c("Observed", hyps[1], hyps[2])
  fill_vals <- c("grey", "white", "white")
  names(fill_vals) <- c("Observed", hyps[1], hyps[2])
  
  error_bar_colors <- c("Observed Error Bar"="black", "Error Bar"="black")
  combined_df <- NA
  if (use_dist_sens_spec) {
    projection_df_list <- tail(projection_df_list, 3)
    sero_dfs <- tail(sero_dfs, 3)
    if (length(sero_dfs) == length(projection_df_list)) {
      names(sero_dfs) <- names(projection_df_list)
    }
  } else {
    projection_df_list <- head(projection_df_list, length(projection_df_list)-3)
  }
  for(sens_spec_val in names(projection_df_list)) {
    df_to_use <- projection_df_list[[sens_spec_val]]$all_ages
    if(length(sero_dfs) > 0) {
      df_to_use <- df_to_use %>% mutate(seroreversion = FALSE)
      df_to_use <- rbind(df_to_use, sero_dfs[[sens_spec_val]]$all_ages %>% mutate(seroreversion = TRUE))
    } else {
      df_to_use <- df_to_use %>% mutate(seroreversion = sero_val)
    }
    if (!use_all_age) {
      df_to_use <- projection_df_list[[sens_spec_val]]$under10
      if(length(sero_dfs) > 0) {
        df_to_use <- df_to_use %>% mutate(seroreversion = FALSE)
        df_to_use <- rbind(df_to_use, sero_dfs[[sens_spec_val]]$under10 %>% mutate(seroreversion = TRUE))
      } else {
        df_to_use <- df_to_use %>% mutate(seroreversion = sero_val)
      }
    }
    df_to_use <- df_to_use %>% select(-sens_mean, -sens_lower, -sens_upper, -spec_mean, -spec_lower, -spec_upper)
    sens_spec_val_to_use = str_replace_all(sens_spec_val, "oti", "oti/kpendjal")
    if(!is.data.frame(combined_df)) {
      combined_df <- df_to_use %>% mutate(sens_spec = sens_spec_val_to_use)
    } else {
      combined_df <- rbind(combined_df, df_to_use %>% mutate(sens_spec = sens_spec_val_to_use))
    }

    filtered_original_df <- original_data %>% mutate(prefecture=tolower(prefecture)) %>% filter(str_detect(sens_spec_val_to_use, prefecture))
    if(use_all_age) {
      combined_df <- rbind(
        combined_df,
        list(
          c(-1, -1),
          rep("Observed", 2), 
          rep(filtered_original_df$all_ages_lb, 2) / 100,
          rep(filtered_original_df$all_ages_ub, 2) / 100,
          rep(filtered_original_df$ov16_prev_all_ages, 2),
          rep(NA, 2),
          rep(NA, 2),
          rep(NA, 2),
          c(FALSE, TRUE),
          rep(sens_spec_val_to_use, 2)
        )
      )
    } else {
      combined_df <- rbind(
        combined_df,
        list(
          # ov16 lb, ub, prev, mf q1, q3, prev, sero, sens spec
          c(-1, -1), 
          rep("Observed", 2), 
          rep(filtered_original_df$children_lb, 2) / 100,
          rep(filtered_original_df$children_ub, 2) / 100,
          rep(filtered_original_df$ov16_prev_children, 2),
          rep(NA, 2),
          rep(NA, 2),
          rep(NA, 2),
          c(FALSE, TRUE),
          rep(sens_spec_val_to_use, 2)
        )
      )
    }
  }
  combined_df_2 <- combined_df %>% 
    separate_wider_delim(sens_spec, delim="_", names=c("sens", "spec")) %>%
    separate_wider_delim(sens, delim=" ", names=c("prefecture", "sens")) %>%
    separate_wider_delim(spec, delim=" ", names=c("to_drop", "spec")) %>%
    select(-to_drop) %>% 
    filter(
      Hypothesis %in% c(
        "Observed", 
        "Mating worm pair with any mf"
      )
    ) %>%
    mutate(
      prefecture = factor(str_to_title(prefecture), levels=c("Oti/Kpendjal", "Keran", "Bassar")),
      Hypothesis = factor(Hypothesis,
                          c(
                            "Observed", 
                            "Mating worm pair with any mf"
                          )),
      error_bar_colors = ifelse(vctr.ctrl.eff < 0, "Observed Error Bar", "Error Bar"),
      seroreversion = ifelse(seroreversion, hyps[2], hyps[1]),
      seroreversion = ifelse(vctr.ctrl.eff < 0, "Observed", seroreversion),
      seroreversion = factor(seroreversion, levels=c("Observed", hyps[1], hyps[2])),
      sens = paste(as.numeric(sens)*100, "%", sep=""),
      spec = paste(as.numeric(spec)*100, "%", sep="")
    )

  if(!use_all_age) {
    combined_df_2 <- combined_df_2 %>% filter(prefecture != "Bassar")
  }

  if (use_oti_100) {
    combined_df_2 <- combined_df_2 %>% filter(
      (prefecture == "Oti/Kpendjal" & vctr.ctrl.eff==0.90) |
      (prefecture == "Keran" & vctr.ctrl.eff==0.90) |
      (prefecture == "Bassar" & vctr.ctrl.eff==0.60) |
      vctr.ctrl.eff == -1
    )
  } else {
    combined_df_2 <- combined_df_2 %>% filter(
      (prefecture == "Oti/Kpendjal" & vctr.ctrl.eff==0.75) |
      (prefecture == "Keran" & vctr.ctrl.eff==0.90) |
      (prefecture == "Bassar" & vctr.ctrl.eff==0.60) |
      vctr.ctrl.eff == -1
    )
  }
  
  plot <- ggplot(data=combined_df_2) +
    geom_bar_pattern(aes(x=prefecture, y=ov16_prev*100, pattern=seroreversion, fill=seroreversion, group=seroreversion), pattern_fill="black", position=position_dodge(width=0.9), width=0.6, stat="identity", color="black", pattern_key_scale_factor=0.25) + 
    geom_errorbar(aes(x=prefecture, ymin=ov16_prev_lb*100, ymax=ov16_prev_ub*100, group=seroreversion, color=error_bar_colors), width=0.3, position=position_dodge(width=0.9)) +
    scale_fill_manual("Model", values=fill_vals) +
    scale_pattern_manual("Model", values=pattern_vals) +
    scale_color_manual("", values=error_bar_colors) +
    xlab("Prefecture") +
    guides(
      color="none",
      fill = guide_legend(title = ""),
      pattern = guide_legend(title = "")
    ) +
    theme_bw() +
    theme(
        plot.title = element_text(size=10, hjust = 0.5),
        axis.title.y = element_text(size=10),
        title = element_text(size=10),
        legend.text = element_text(size=6),
        legend.title = element_text(size=8),
        legend.key.size = unit(0.8, 'lines'),
        legend.position = "bottom",  # Set legend to the bottom
        legend.direction = "horizontal",
        axis.text.y = element_text(size=6),
        axis.text.x = element_text(size=6, angle=70, vjust=0.5),
        strip.placement = "outside",
        panel.border = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        axis.line.x = element_line(color = "black"),
        axis.line.y = element_line(color = "black"),
        strip.text.y = element_text(angle=0),
        axis.line.y.right = element_blank()
    ) +
    geom_segment(aes(x=0.55, xend=1.45, y=-5, yend=-5), color="black", size=0.1) +
    geom_segment(aes(x=0.55, xend=0.55, y=0, yend=-5), color="black", size=0.1) +
    geom_segment(aes(x=1.45, xend=1.45, y=0, yend=-5), color="black", size=0.1) + 
    geom_segment(aes(x=1.55, xend=2.45, y=-5, yend=-5), color="black", size=0.1) +
    geom_segment(aes(x=1.55, xend=1.55, y=0, yend=-5), color="black", size=0.1) +
    geom_segment(aes(x=2.45, xend=2.45, y=0, yend=-5), color="black", size=0.1)
  if (!use_dist_sens_spec) {
    plot <- plot +
      ggtitle("Specificity") +
      facet_grid(sens ~ spec) +
      scale_y_continuous(
        paste("Anti-Ov16", ylab, "seroprevalence (%)"),
        limits = c(-5, max(combined_df_2$ov16_prev_ub*100)),
        breaks=seq(0, 60, 20),
        sec.axis = sec_axis(~ . , name = "Sensitivity", breaks = NULL, labels = NULL)
      )
  } else {
    plot <- plot +
      scale_y_continuous(
        paste("Anti-Ov16", ylab, "seroprevalence (%)"),
        limits = c(-5, max(combined_df_2$ov16_prev_ub*100)),
        breaks=seq(0, 60, 20)
      )
  }
  if(use_all_age) {
    plot <- plot + 
      geom_segment(aes(x=2.55, xend=3.45, y=-5, yend=-5), color="black", size=0.1) +
      geom_segment(aes(x=2.55, xend=2.55, y=0, yend=-5), color="black", size=0.1) +
      geom_segment(aes(x=3.45, xend=3.45, y=0, yend=-5), color="black", size=0.1)
  }
  print(plot)
  ggsave(paste("images/images_", run_version, "/togo_sens_spec_analysis_bar_", descriptor, ".svg", sep=""), plot, units="in", height=5, width=6, dpi=300)
}

makePrefectureBarSensSpecBestFit(groupedVillageData, k3_instant_seroreversion_simulation_summary_combined_sens_spec_list, TRUE, "both_all_ages_best_vc", k3_gradual_seroreversion_simulation_summary_combined_sens_spec_list, hyps=c("H4ii", "H4iii"))

makePrefectureBarSensSpecBestFit(groupedVillageData, k3_instant_seroreversion_simulation_summary_combined_sens_spec_list, TRUE, "both_all_ages_best_vc_dist_sens_spec", k3_gradual_seroreversion_simulation_summary_combined_sens_spec_list, use_dist_sens_spec=TRUE, hyps=c("H4ii", "H4iii"))

makePrefectureBarSensSpecBestFit(groupedVillageData, k3_gradual_seroreversion_simulation_summary_combined_sens_spec_list, TRUE, "finite_all_ages_best_vc_dist_sens_spec", use_dist_sens_spec=TRUE, sero_val=TRUE)

makePrefectureBarSensSpecBestFit(groupedVillageData, k3_instant_seroreversion_simulation_summary_combined_sens_spec_list, FALSE, "both_under_10_best_vc", k3_gradual_seroreversion_simulation_summary_combined_sens_spec_list, hyps=c("H4ii", "H4iii"))

makePrefectureBarSensSpecBestFit(groupedVillageData, k3_instant_seroreversion_simulation_summary_combined_sens_spec_list, FALSE, "both_under_10_best_vc_dist_sens_spec", k3_gradual_seroreversion_simulation_summary_combined_sens_spec_list, use_dist_sens_spec=TRUE, hyps=c("H4ii", "H4iii"))

makePrefectureBarSensSpecBestFit(groupedVillageData, k3_gradual_seroreversion_simulation_summary_combined_sens_spec_list, FALSE, "finite_under_10_best_vc_dist_sens_spec", use_dist_sens_spec=TRUE, sero_val=TRUE)

```

#### Age Groups Using Just Best Fit VCs
```{r}
# best_fit_sens_spec <- c("70%, 95%", "70%, 85%")
filterHypotheses <- function(data) {
  # actual_hyps <- c("Patent Infection")
  # data <- data %>% filter(Hypothesis %in% actual_hyps) %>% mutate(
  #   Hypothesis = "Mating worm pair with any mf"
  # )
  return(data)
}
makeAgeGroupGraphsSensSpecBestFit <- function(originalData, projection_df_list, descriptor, facet_value="sens ~ spec", facet_1, facet_2, best_fit_sens_spec) {
  originalData <- originalData %>% filter(age_groups != 0.0)
  combined_df <- NA
  for(sens_spec_val in names(projection_df_list)) {
    if(!is.data.frame(combined_df)) {
      combined_df <- projection_df_list[[sens_spec_val]] %>% mutate(sens_spec = sens_spec_val)
    } else {
      combined_df <- rbind(combined_df, projection_df_list[[sens_spec_val]] %>% mutate(sens_spec = sens_spec_val))
    }
  }

  combined_df_2 <- combined_df %>% separate_wider_delim(sens_spec, delim="_", names=c("sens", "spec"))

  tmp_projection_data <- combined_df_2 %>% 
    mutate(vctr.ctrl.eff = paste(as.numeric(vctr.ctrl.eff)*100, "%", sep="")) %>% 
    mutate(
      sens = paste(as.numeric(sens)*100, "%", sep=""),
      spec = paste(as.numeric(spec)*100, "%", sep="")
    ) %>% filterHypotheses() %>%
    mutate(
      sero_type = factor(sero_type, levels=c("H4i", "H4ii", "Midpoint", "H4iii")),
      sens_spec = paste0(sens, ", ", spec)
    ) %>% filter(
      sens_spec %in% best_fit_sens_spec
    )
  
    

    color_vals <- c("H4i"="black", "H4ii"="black", "Midpoint"="black", "H4iii"="black")
    linetype_vals <- c("H4i"="solid", "H4ii"="dotted", "Midpoint"="dashed", "H4iii"="solid")
    p1 <- ggplot() + 
      geom_line(
        aes(x=age_groups, y=ov16_prev*100, 
            linetype=sero_type,
            color=sero_type
            ), 
        size=0.5, data=tmp_projection_data
      ) +
      geom_ribbon(
        aes(x=age_groups, ymin=ov16_q1*100, ymax=ov16_q3*100,
            fill=sero_type,
            linetype=sero_type
            ),
        alpha=0.1,
        size=0.1,
        data=tmp_projection_data
      ) +
      geom_point(
        aes(x=age_groups, y=ov16_seroprev*100), 
        color="black", alpha=0.5, data=originalData, size=0.5
      ) +
      geom_errorbar(
        aes(x=age_groups, ymin=ov16_wilson_lb*100, ymax=ov16_wilson_ub*100), 
        width=2.5, alpha=0.5, color="black", data=originalData
      ) +
      xlab("Age (years)") + ylab("Anti-Ov16 seroprevalence (%)") +
      scale_color_manual("", values=color_vals) +
      scale_fill_manual("", values=color_vals) +
      scale_linetype_manual("", values=linetype_vals) +
      theme_bw() +
      # facet_grid(facet_value) +
      scale_y_continuous(
        limits=c(0, 101), 
        breaks=seq(0, 100, 25), 
        sec.axis = sec_axis(~ . , name = facet_1, breaks = NULL, labels = NULL)
      ) +
      scale_x_continuous(
        limits=c(0, 81), 
        breaks=seq(0, 100, 20) 
      ) +
      # ggtitle(facet_2) +
      theme_bw() +
      theme(
        plot.title = element_text(size=10, hjust = 0.5),
        axis.title.y = element_text(size=10),
        title = element_text(size=10),
        legend.text = element_text(size=6),
        legend.title = element_text(size=8),
        legend.key.size = unit(0.8, 'lines'),
        legend.position = "bottom",  # Set legend to the bottom
        legend.direction = "horizontal",
        axis.text.y = element_text(size=6),
        axis.text.x = element_text(size=6),
        strip.placement = "outside",
        panel.grid.minor = element_blank(),
        axis.line.x = element_line(color = "black"),
        axis.line.y = element_line(color = "black"),
        strip.text.y = element_text(angle=0),
        axis.line.y.right = element_blank()
      )
    ggsave(paste("images/images_", run_version, "/togo_sens_spec_analysis_", descriptor, ".svg", sep=""), p1, units="in", height=4, width=5.5, dpi=300)
    print(p1)
}

# best fit with scenarios from Luis' paper
best_fit_vc <- list()
best_fit_vc_100_mount <- selectRunsFromAllPrefectures(
 simulatedOti_k3_100_mount %>% filter(vctr.ctrl.eff == 0.75) %>% mutate(run_num = run_num - 1500, vctr.ctrl.eff=0.6),
 (simulatedKeran_k3_100_mount %>% filter(vctr.ctrl.eff == 0.90) %>% mutate(run_num = run_num - 2, vctr.ctrl.eff=0.6)),
 simulatedBassar_k3_100_mount %>% filter(vctr.ctrl.eff == 0.60),
 sampleNum=sample_num_ov16) %>% mutate(sero_type="i")

best_fit_vc_instant_seroreversion <- selectRunsFromAllPrefectures(
 simulatedOti_k3_instant_seroreversion %>% filter(vctr.ctrl.eff == 0.75) %>% mutate(run_num = run_num - 1500, vctr.ctrl.eff=0.75),
 (simulatedKeran_k3_instant_seroreversion %>% filter(vctr.ctrl.eff == 0.90) %>% mutate(run_num = run_num - 2, vctr.ctrl.eff=0.75)),
 simulatedBassar_k3_instant_seroreversion %>% filter(vctr.ctrl.eff == 0.60) %>% mutate(vctr.ctrl.eff=0.75),
 sampleNum=sample_num_ov16) %>% mutate(sero_type="ii")

best_fit_vc_finite_seroreversion <- selectRunsFromAllPrefectures(
 simulatedOti_k3_gradual_seroreversion %>% filter(vctr.ctrl.eff == 0.75) %>% mutate(run_num = run_num - 1500, vctr.ctrl.eff=0.90),
 (simulatedKeran_k3_gradual_seroreversion %>% filter(vctr.ctrl.eff == 0.90) %>% mutate(run_num = run_num - 2, vctr.ctrl.eff=0.90)),
 simulatedBassar_k3_gradual_seroreversion %>% filter(vctr.ctrl.eff == 0.60) %>% mutate(vctr.ctrl.eff=0.90),
 sampleNum=sample_num_ov16) %>% mutate(sero_type="iii")
best_fit_total = rbind(
  best_fit_vc_100_mount,
  best_fit_vc_instant_seroreversion,
  best_fit_vc_finite_seroreversion
)
for (sens_spec_val in sens_spec_options) {
  print(sens_spec_val)
  tmp <- summarizeSimulationData(best_fit_total %>% mutate(sens = sens_spec_val[1], spec=sens_spec_val[2]), sens_spec_val, groupBySex=FALSE) %>% mutate(sero_type=case_when(
    vctr.ctrl.eff == 0.6 ~ "H4i",
    vctr.ctrl.eff == 0.75 ~ "H4ii",
    TRUE ~ "H4iii")
  )
  tmp_hi <- tmp %>% filter(sero_type == "H4i")
  tmp_hii <- tmp %>% filter(sero_type == "H4ii")
  tmp_hiii <- tmp %>% filter(sero_type == "H4iii") %>% select(age_groups, Hypothesis, ov16_prev)
  tmp_midpoint <- tmp_hii %>% left_join(tmp_hiii, by=c("age_groups", "Hypothesis")) %>% mutate(ov16_prev = (ov16_prev.x + ov16_prev.y) / 2, sero_type="Midpoint") %>% select(-ov16_prev.x, -ov16_prev.y) %>% mutate(
    ov16_q1=NaN, ov16_q3=NaN
  )
 best_fit_vc[[paste(sens_spec_val, collapse="_")]] <- rbind(tmp, tmp_midpoint)
}

tmp <- summarizeSimulationData(best_fit_total, sens_spec_from_dist, groupBySex=FALSE) %>% mutate(sero_type=case_when(
  vctr.ctrl.eff == 0.6 ~ "H4i",
  vctr.ctrl.eff == 0.75 ~ "H4ii",
  TRUE ~ "H4iii")
)
tmp_hi <- tmp %>% filter(sero_type == "H4i")
tmp_hii <- tmp %>% filter(sero_type == "H4ii")
tmp_hiii <- tmp %>% filter(sero_type == "H4iii") %>% select(age_groups, Hypothesis, ov16_prev)
tmp_midpoint <- tmp_hii %>% left_join(tmp_hiii, by=c("age_groups", "Hypothesis")) %>% mutate(ov16_prev = (ov16_prev.x + ov16_prev.y) / 2, sero_type="Midpoint") %>% select(-ov16_prev.x, -ov16_prev.y) %>% mutate(ov16_q1=NaN, ov16_q3=NaN)
best_fit_vc[[
  paste0(round(tmp$sens_mean[1], 2), "_", round(tmp$spec_mean[1], 2))
]] <- rbind(tmp, tmp_midpoint)


makeAgeGroupGraphsSensSpecBestFit(togoOv16Data, lapply(best_fit_vc, function(x) {filter(x, sero_type != "H4i" & age_groups != 2.5)}), "best_vc_all", "~sens_spec", "", "Sensitivity, Specificity", best_fit_sens_spec = paste0(round(tmp$sens_mean[1], 2)*100, "%, ", round(tmp$spec_mean[1], 2)*100, "%"))

best_fit_vc_h4ii <- lapply(best_fit_vc, function(df) {
  df %>% filter(sero_type == "H4iii")
})
makeAgeGroupGraphsSensSpecBestFit(togoOv16Data, best_fit_vc_h4ii, "best_vc_h4iii", "~sens_spec", "", "Sensitivity, Specificity", best_fit_sens_spec = paste0(round(tmp$sens_mean[1], 2)*100, "%, ", round(tmp$spec_mean[1], 2)*100, "%"))

best_fit_vc_resids <- c()
for(sens_spec in sens_spec_options) {
  print(sens_spec)
  new_result <- rbind(
      custom_calc_resid(togoOv16Data %>% filter(age_groups > 0), data_manip_resid(best_fit_vc_100_mount, sens_spec), "No Seroreversion"),
      custom_calc_resid(togoOv16Data %>% filter(age_groups > 0),
                        data_manip_resid(best_fit_vc_finite_seroreversion %>% filter(), sens_spec) %>% 
                          left_join(
                            data_manip_resid(best_fit_vc_100_mount, sens_spec) %>% select(-vctr.ctrl.eff), by=c("run_num", "Hypothesis", "age_groups")
                          ) %>%
                          mutate(
                            ov16_prev = (ov16_prev.x + ov16_prev.y) / 2
                          ) %>%
                          select(-ov16_prev.x, ov16_prev.y), 
                        "Midpoint Seroreversion"),
      custom_calc_resid(togoOv16Data %>% filter(age_groups > 0), data_manip_resid(best_fit_vc_finite_seroreversion %>% filter(), sens_spec), "Finite Seroreversion")
  )
  new_result$sens_spec <- paste0(sens_spec, collapse=", ")
  if (length(best_fit_vc_resids) == 0) {
    best_fit_vc_resids <- new_result
  } else {
    best_fit_vc_resids <- rbind(
      best_fit_vc_resids,
      new_result
    )
  }
}

new_result <- rbind(
    custom_calc_resid(togoOv16Data %>% filter(age_groups > 0), data_manip_resid(best_fit_vc_100_mount, c(-1, -1)), "No Seroreversion"),
    custom_calc_resid(togoOv16Data %>% filter(age_groups > 0),
                      data_manip_resid(best_fit_vc_finite_seroreversion %>% filter(), c(-1, -1)) %>% 
                        left_join(
                          data_manip_resid(best_fit_vc_100_mount, c(-1, -1)) %>% select(-vctr.ctrl.eff), by=c("run_num", "Hypothesis", "age_groups")
                        ) %>%
                        mutate(
                          ov16_prev = (ov16_prev.x + ov16_prev.y) / 2
                        ) %>%
                        select(-ov16_prev.x, ov16_prev.y), 
                      "Midpoint Seroreversion"),
    custom_calc_resid(togoOv16Data %>% filter(age_groups > 0), data_manip_resid(best_fit_vc_finite_seroreversion %>% filter(), c(-1, -1)), "Finite Seroreversion")
)
new_result$sens_spec <- paste0(c(-1, -1), collapse=", ")
best_fit_vc_resids <- rbind(
  best_fit_vc_resids,
  new_result
)
process_resids(best_fit_vc_resids, FALSE)
process_resids(best_fit_vc_resids, TRUE)
```
